---
title: "Diabetes WDF baseline and Followup Merged"
author: "Reinpeter"
date: "`r Sys.Date()`"
output:
  word_document: 
    fig_width: 12
    fig_height: 8
    number_sections: yes
  pdf_document:
    fig_width: 12
    fig_height: 8
    number_sections: yes
  html_document:
    toc: yes
    toc_depth: 4
    number_sections: yes
---


```{r setup, results="hide", include=FALSE}

## Set Chunk requirements
knitr::opts_chunk$set(#include = TRUE,
                      echo=FALSE, message = FALSE, warning = FALSE)

```

```{r setting working directory, include=FALSE, results = "hide"}

## Setting work directory

setwd(".")


```


```{r loading relevant packages, include=FALSE, results = "hide"}

#library we need
libs_diabetes <- c("googledrive" ,"tidyverse", "haven", "janitor", "knitr", "lubridate", "plotly", "gtsummary", "flextable",
                   "sjlabelled", "rstatix", "lme4", "lmerTest")

#install missing libraries

inatalled_libs_diabetes <- libs_diabetes  %in% rownames(installed.packages())
if (any(inatalled_libs_diabetes==F)) {
  install.packages(libs_diabetes[!inatalled_libs_diabetes])
}

#load libraries

invisible(lapply(libs_diabetes, library, character.only=T))


set_gtsummary_theme(list(
  "tbl_summary-fn:percent_fun" = function(x) style_percent(x, digits = 1),
  "tbl_summary-str:categorical_stat" = "{n} ({p}%)"
))
# Setting `Compact` theme
theme_gtsummary_compact()

```


```{r importing saved Rdata files, results="hide", include=FALSE}

#load .Rdata files

wdfbaseline_followup_list <- list.files(path = ".", pattern = "*.RData", full.names = TRUE)

invisible(lapply(wdfbaseline_followup_list, load, .GlobalEnv))

```

```{r assigning variable labels}

#Creating a named vector to quickly assign the variable labels using baseline variable labels

diabetes_baseline_followup_variable_attr <- as.data.frame(labelled::generate_dictionary(diabetes_baseline_final_clean))

diabetes_baseline_followup_labels <- diabetes_baseline_followup_variable_attr%>%
  dplyr::select(variable, label)%>%
  deframe()

```

```{r subset data, results="hide", include=FALSE}

#subset baseline and followup data with same columns

diabetes_baseline_final_clean_merge <- diabetes_baseline_final_clean%>%
  dplyr::select(study_id:wdf_q1_12, wdf_q2_1:wdf_q2_4, wdf_q2_5:wdf_q2_8isp, wdf_q2_9:wdf_q2_10, wdf_q2_11a:wdf_q2_13, 
                wdf_q2_14:wdf_q2_15f, wdf_q2_16a, wdf_q2_16b, wdf_q2_16c, wdf_q2_16d, wdf_q2_16e, wdf_q2_16f, wdf_q2_16g,
                wdf_q2_16h, wdf_q2_16i, wdf_q2_17a:wdf_q2_19sp, wdf_q3_1:wdf_q3_10, wdf_q3_14:wdf_q3_17f,
                wdf_q5_0a:wdf_q5_11, wdf_q1_4_age:wdf_q2_11a_b_years_group, wdf_q5_1_2_3a:wdf_q5_10_group )

diabetes_followup_final_clean_merge <- diabetes_followup_final_clean%>%
  dplyr::select(study_id:wdf_q1_12_followup, wdf_q2_1_followup:wdf_q2_4_followup, wdf_q2_5_followup:wdf_q2_8isp_followup,
                wdf_q2_9_followup:wdf_q2_10_followup, wdf_q2_11a_followup:wdf_q2_13_followup, wdf_q2_14_followup:wdf_q2_15f_followup,
                wdf_q2_16a_followup:wdf_q2_16i_followup, wdf_q2_17a_followup, wdf_q2_18a_followup, wdf_q2_17b_followup:wdf_q2_19sp_followup,
                wdf_q3_1_followup:wdf_q3_3_followup, wdf_q3_4_followup, wdf_q3_5a_followup:wdf_q3_8_followup, wdf_q3_9_followup, wdf_q3_10_followup,
                wdf_q3_14_followup, wdf_q3_15_followup, wdf_q3_16_followup:wdf_q3_17f_followup, 
                wdf_q5_0a_followup:wdf_q5_4_followup, wdf_q5_5a_followup, wdf_q5_5b_followup, wdf_q5_61_followup:wdf_q5_11_followup,
                wdf_q1_4_followup_age:wdf_q5_10_followup_group)

```


```{r merging data rowwise, results="hide", include=FALSE}

wdfbaseline_followup_clean <- rbind(diabetes_baseline_final_clean_merge,
                   data.table::setnames(diabetes_followup_final_clean_merge,
                                        names(diabetes_baseline_final_clean_merge)
                   ))%>%
  mutate(wdf_q1_9 = ifelse(wdf_q1_9 == "B", "Baseline", wdf_q1_9),
    wdf_q1_9 = factor(wdf_q1_9, levels = c("Baseline", "Six month follow-up", "One year follow-up"))
    )%>%
  labelled::set_variable_labels(!!!diabetes_baseline_followup_labels[names(diabetes_baseline_followup_labels) %in% names(.)]) #labeling variables from data dictionary

```


```{r subset data for etl, results="hide", include=FALSE}

wdfbaseline_followup_clean_etl <- wdfbaseline_followup_clean%>%
  dplyr::select(study_id:wdf_q1_2, wdf_q1_4:wdf_q1_5, wdf_q1_9, wdf_q1_10,
                wdf_q2_1:wdf_q2_5, wdf_q2_9:wdf_q2_13, wdf_q2_17a:wdf_q2_19f, wdf_q5_0a:wdf_q5_11
  )

wdfbaseline_followup_clean_etl1 <- wdfbaseline_followup_clean%>%
  dplyr::select(study_id:wdf_q1_2, wdf_q1_4:wdf_q1_5, wdf_q1_9, wdf_q1_10,
                wdf_q2_1:wdf_q2_5, wdf_q2_9:wdf_q2_13, wdf_q2_17a:wdf_q2_19f, wdf_q5_0a:wdf_q5_11
  )%>%
  sjlabelled:::label_to_colnames() #variable labels to column names.
  

readr::write_csv(wdfbaseline_followup_clean_etl,"wdfbaseline_followup_clean_etl.csv", na="")

readr::write_csv(wdfbaseline_followup_clean_etl1,"wdfbaseline_followup_clean_etl1.csv", na="")

```


# **Introduction**

This study titled [**Improving the lives of diabetics in Nairobi's slum through access to quality health care**](https://microdataportal.aphrc.org/index.php/catalog/75) was under the **Health and Well-Being (HaW) Theme** and aimed to improve the management of diabetes and other comorbidities with emphasis on the use of integrated guidelines and patient empowerment. It was carried out from Individual respondents living in Korogocho and Viwandani informal settlements in Nairobi.

This analysis aims to assess impact of interventions on clinical parameters (i.e weight, bmi, systolic blood pressure, diastolic blood pressure, waist measurements, hip measurements, waist to hip ratio, blood glucose)

```{r diabetes baseline followup final data for analysis, results="hide", include=FALSE}

# make baseline and 6month follow up dataset with variables for descriptive and inferential statistics
  wdfbaseline_followup_final_analysis <- wdfbaseline_followup_clean%>%
  dplyr::select( study_id, wdf_q1_9:wdf_q1_12,
    #socio-demographics
    wdf_q1_5, wdf_q1_4_age_group,
    #History of medical conditions and treatment
    wdf_q2_1, wdf_q2_9, wdf_q2_19a:wdf_q2_19f,
    #Lifestyle history/Health behaviour
    wdf_q3_2, wdf_q3_7, wdf_q3_10, wdf_q3_14,
    #Clinical and anthropometric measurements
    wdf_q5_0a:wdf_q5_0c, wdf_q5_8a, wdf_q5_8b, wdf_q5_10, wdf_q5_1_2_3a, wdf_q5_1_2_3b, wdf_q5_5a_b, wdf_q5_6_7, 
    wdf_q5_5_6_7_bmi, wdf_q5_8a_b_waist_hip_ratio
                )%>%
  filter( wdf_q1_9 != "One year follow-up")%>%
  mutate(across(c(wdf_q2_1, wdf_q2_9, wdf_q3_2, wdf_q3_7, wdf_q3_10, wdf_q3_14, wdf_q5_0a:wdf_q5_0c), ~fct_rev(.x)),
         across(c(wdf_q2_19a:wdf_q2_19f), ~factor(.x, levels = c("No", "Yes", "Dont Know"))))%>%
  mutate_if(is.factor, ~fct_drop(.x #, only = c("")
            ))%>% #drop unused factor levels
  labelled::set_variable_labels(!!!diabetes_baseline_followup_labels[names(diabetes_baseline_followup_labels) %in% names(.)]) #labeling variables from data dictionary

diabetes_baseline_followup_variable_attr <- as.data.frame(labelled::generate_dictionary(wdfbaseline_followup_final_analysis))%>%
  dplyr::select(variable, label)

```


# **Descriptives**

## Follow-up Rate

```{r final variables by data collection round}

 tbl_summary(wdfbaseline_followup_final_analysis%>%
    dplyr::select(-study_id),
              by = wdf_q1_9,
                      type = list(
                        all_dichotomous() ~ "categorical"
                         ,all_continuous() ~ "continuous2"
                        )
                      , statistic = all_continuous() ~ c(
                                      "{mean} ({sd})", 
                                      "{median} ({p25}, {p75})", 
                                      "{min}, {max}")
                       , digits = list(all_continuous() ~ 2, 
                                      all_categorical() ~ c(0, 1))
                      ,percent = "column" #"column", "row", or "cell"
                      , missing = "always" #list missing data separately #ifany #no #always
                      ,missing_text = "Missing"
                      ) %>% 
  modify_header(label = "**Variables**") %>% # update the column header
  bold_labels() %>%
  italicize_levels()%>%
  #add_n( statistic = "{n}", col_label = "**n**", last = FALSE, footnote = FALSE)%>% # add column with total number of non-missing observations
  #add_overall() %>%
  #add_difference() %>% #add column for difference between two group, confidence interval, and p-value
  modify_spanning_header(c("stat_1", "stat_2") ~ "**Data Collection Round**")%>%
  modify_footnote(
    all_stat_cols() ~ "Mean (SD); Median (IQR); Range; Frequency (%)"
  )%>%
  as_flex_table() #covert gtsummary object to flex table object. 

```


## Normality of continous variables

```{r}

  wdfbaseline_followup_final_analysis%>%
    dplyr::select(wdf_q1_9, wdf_q5_8a, wdf_q5_8b, wdf_q5_10, wdf_q5_1_2_3a, wdf_q5_1_2_3b, wdf_q5_5a_b, wdf_q5_6_7, 
    wdf_q5_5_6_7_bmi, wdf_q5_8a_b_waist_hip_ratio )%>%
  #sjlabelled:::label_to_colnames() %>% #variable labels to column names.
  group_by(wdf_q1_9)%>%
  shapiro_test(wdf_q5_8a, wdf_q5_8b, wdf_q5_10, wdf_q5_1_2_3a, wdf_q5_1_2_3b, wdf_q5_5a_b, wdf_q5_6_7, 
    wdf_q5_5_6_7_bmi, wdf_q5_8a_b_waist_hip_ratio)%>%
  left_join(as.data.frame(labelled::generate_dictionary(wdfbaseline_followup_final_analysis))%>%
  dplyr::select(variable, label),
  by = c("variable" = "variable"))%>%
  kable()

```

# **Inferential statistics**

## Paired tests

### Overall

```{r paired test overall}

overall_paired <- wdfbaseline_followup_final_analysis%>%
  dplyr::select(study_id, wdf_q1_9, wdf_q5_8a, wdf_q5_8b, wdf_q5_10, wdf_q5_1_2_3a, wdf_q5_1_2_3b, wdf_q5_6_7, 
    wdf_q5_5_6_7_bmi, wdf_q5_8a_b_waist_hip_ratio)%>%
  pivot_longer(
    cols = !c(study_id, wdf_q1_9),
    names_to = "clinical_parameters",
    values_to = "value"
  )%>%
  drop_na()%>%
  group_by(study_id, clinical_parameters)%>%
  filter(n()==2)%>%
  ungroup()%>%
  mutate(clinical_parameters = as_factor(clinical_parameters))%>%
  nest_by(clinical_parameters)%>%
  mutate(table_out = list(tbl_summary(data,
               by = wdf_q1_9, include = -study_id,
                       type = list(
                         c(value) ~ "continuous2",
                          all_continuous() ~ "continuous2")
                       , statistic = all_continuous() ~ c(
                                      "{mean} ({sd})", 
                                      "{median} ({p25}, {p75})", 
                                      "{min}, {max}")
                       , digits = all_continuous() ~ 2
                       , missing = "ifany" # don't list missing data separately #ifany #no
                       ,missing_text = "Missing"
                       ) %>% 
   modify_header(label = "**Differences Overall**") %>% # update the column header
   bold_labels() %>%
   italicize_levels()%>%
   add_p(pvalue_fun = ~style_pvalue(.x, digits = 3),
         test = list(value ~ "paired.wilcox.test"), group = study_id ) %>%
   bold_p(t= 0.05) %>% # bold p-values under a given threshold (default 0.05)
   modify_footnote(
     all_stat_cols() ~ "Mean (SD); Median (IQR); Range"
   )
    ))

tbl_merge(overall_paired$table_out,
    tab_spanner = c("**Systolic Blood pressure**", "**Diastolic Blood pressure**", "**Blood glucose (mmol/L)**", "**BMI (kg/m2)**",
                    "**Weight in kgs**", "**Waist circumference**", "**Waist-to-hip ratio**", "**Hip circumference**"))

```

### Gender

```{r paired test gender}

gender_paired <- wdfbaseline_followup_final_analysis%>%
  dplyr::select(study_id, wdf_q1_9, wdf_q1_5, wdf_q5_8a, wdf_q5_8b, wdf_q5_10, wdf_q5_1_2_3a, wdf_q5_1_2_3b, wdf_q5_6_7, 
    wdf_q5_5_6_7_bmi, wdf_q5_8a_b_waist_hip_ratio)%>%
  pivot_longer(
    cols = !c(study_id, wdf_q1_9, wdf_q1_5),
    names_to = "clinical_parameters",
    values_to = "value"
  )%>%
  drop_na()%>%
  group_by(study_id, clinical_parameters, wdf_q1_5)%>%
  filter(n()==2)%>%
  ungroup()%>%
  mutate(clinical_parameters = as_factor(clinical_parameters))%>%
  nest_by(clinical_parameters)%>%
  mutate(table_out = list(
    tbl_strata(data,
               strata = wdf_q1_5,
               .tbl_fun = ~ .x %>%
        tbl_summary(
               by = wdf_q1_9, include = -study_id,
                       type = list(
                         c(value) ~ "continuous2",
                          all_continuous() ~ "continuous2")
                       , statistic = all_continuous() ~ c(
                                      "{mean} ({sd})", 
                                      "{median} ({p25}, {p75})", 
                                      "{min}, {max}")
                       , digits = all_continuous() ~ 2
                       , missing = "ifany" # don't list missing data separately #ifany #no
                       ,missing_text = "Missing"
                       ) %>% 
   modify_header(label = "**Differences Gender (1=Female, 2=Male)**") %>% # update the column header
   bold_labels() %>%
   italicize_levels()%>%
   add_p(pvalue_fun = ~style_pvalue(.x, digits = 3),
         test = list(value ~ "paired.wilcox.test"), group = study_id ) %>%
   bold_p(t= 0.05) %>% # bold p-values under a given threshold (default 0.05)
   modify_footnote(
     all_stat_cols() ~ "Mean (SD); Median (IQR); Range"
   )
   )
   ))

tbl_merge(gender_paired$table_out,
    tab_spanner = c("**Systolic Blood pressure**", "**Diastolic Blood pressure**", "**Blood glucose (mmol/L)**", "**BMI (kg/m2)**",
                    "**Weight in kgs**", "**Waist circumference**", "**Waist-to-hip ratio**", "**Hip circumference**"))

```

### Diabetes

```{r paired test diabetes}

diabetes_paired <- wdfbaseline_followup_final_analysis%>%
  dplyr::select(study_id, wdf_q1_9, wdf_q2_1, wdf_q5_8a, wdf_q5_8b, wdf_q5_10, wdf_q5_1_2_3a, wdf_q5_1_2_3b, wdf_q5_6_7, 
    wdf_q5_5_6_7_bmi, wdf_q5_8a_b_waist_hip_ratio)%>%
  pivot_longer(
    cols = !c(study_id, wdf_q1_9, wdf_q2_1),
    names_to = "clinical_parameters",
    values_to = "value"
  )%>%
  drop_na()%>%
  group_by(study_id, clinical_parameters, wdf_q2_1)%>%
  filter(n()==2)%>%
  ungroup()%>%
  mutate(clinical_parameters = as_factor(clinical_parameters))%>%
  nest_by(clinical_parameters)%>%
  mutate(table_out = list(
    tbl_strata(data,
               strata = wdf_q2_1,
               .tbl_fun = ~ .x %>%
        tbl_summary(
               by = wdf_q1_9, include = -study_id,
                       type = list(
                         c(value) ~ "continuous2",
                          all_continuous() ~ "continuous2")
                       , statistic = all_continuous() ~ c(
                                      "{mean} ({sd})", 
                                      "{median} ({p25}, {p75})", 
                                      "{min}, {max}")
                       , digits = all_continuous() ~ 2
                       , missing = "ifany" # don't list missing data separately #ifany #no
                       ,missing_text = "Missing"
                       ) %>% 
   modify_header(label = "**Differences (1=Not Diabetic, 2=Diabetic)**") %>% # update the column header
   bold_labels() %>%
   italicize_levels()%>%
   add_p(pvalue_fun = ~style_pvalue(.x, digits = 3),
         test = list(value ~ "paired.wilcox.test"), group = study_id ) %>%
   bold_p(t= 0.05) %>% # bold p-values under a given threshold (default 0.05)
   modify_footnote(
     all_stat_cols() ~ "Mean (SD); Median (IQR); Range"
   )
   )
   ))

tbl_merge(diabetes_paired$table_out,
    tab_spanner = c("**Systolic Blood pressure**", "**Diastolic Blood pressure**", "**Blood glucose (mmol/L)**", "**BMI (kg/m2)**",
                    "**Weight in kgs**", "**Waist circumference**", "**Waist-to-hip ratio**", "**Hip circumference**"))

```

### Hypertension

```{r paired test hypertension}

hypertension_paired <- wdfbaseline_followup_final_analysis%>%
  dplyr::select(study_id, wdf_q1_9, wdf_q2_9, wdf_q5_8a, wdf_q5_8b, wdf_q5_10, wdf_q5_1_2_3a, wdf_q5_1_2_3b, wdf_q5_6_7, 
    wdf_q5_5_6_7_bmi, wdf_q5_8a_b_waist_hip_ratio)%>%
  pivot_longer(
    cols = !c(study_id, wdf_q1_9, wdf_q2_9),
    names_to = "clinical_parameters",
    values_to = "value"
  )%>%
  drop_na()%>%
  group_by(study_id, clinical_parameters, wdf_q2_9)%>%
  filter(n()==2)%>%
  ungroup()%>%
  mutate(clinical_parameters = as_factor(clinical_parameters))%>%
  nest_by(clinical_parameters)%>%
  mutate(table_out = list(
    tbl_strata(data,
               strata = wdf_q2_9,
               .tbl_fun = ~ .x %>%
        tbl_summary(
               by = wdf_q1_9, include = -study_id,
                       type = list(
                         c(value) ~ "continuous2",
                          all_continuous() ~ "continuous2")
                       , statistic = all_continuous() ~ c(
                                      "{mean} ({sd})", 
                                      "{median} ({p25}, {p75})", 
                                      "{min}, {max}")
                       , digits = all_continuous() ~ 2
                       , missing = "ifany" # don't list missing data separately #ifany #no
                       ,missing_text = "Missing"
                       ) %>% 
   modify_header(label = "**Differences (1=Not Hypertensive, 2=Hypertensive)**") %>% # update the column header
   bold_labels() %>%
   italicize_levels()%>%
   add_p(pvalue_fun = ~style_pvalue(.x, digits = 3),
         test = list(value ~ "paired.wilcox.test"), group = study_id ) %>%
   bold_p(t= 0.05) %>% # bold p-values under a given threshold (default 0.05)
   modify_footnote(
     all_stat_cols() ~ "Mean (SD); Median (IQR); Range"
   )
   )
   ))

tbl_merge(hypertension_paired$table_out,
    tab_spanner = c("**Systolic Blood pressure**", "**Diastolic Blood pressure**", "**Blood glucose (mmol/L)**", "**BMI (kg/m2)**",
                    "**Weight in kgs**", "**Waist circumference**", "**Waist-to-hip ratio**", "**Hip circumference**"))

```

## Linear mixed effect model

Linear Mixed model adjusting for all response variables allowing intercept to vary by invividual id.

The REML = TRUE argument is used to specify that the REstricted Maximum Likelihood criterion be used rather than the loglikelihood criterion for optimization of parameter estimates.

### Random intercept model

Random intercept model - Each individual is assigned a different intercept as we give the model with “(1|individual_id)”.Note also that the fixed effects (baseline-followup and other predictor variables) are all the same for all individual_id. We account for baseline-differences in response variables (bmi, bloodglucose..etc), but we assume that whatever the effect of intervention is, it’s going to be the same for all subjects and items.

```{r mixed model}

diabetes_mixed_model <- wdfbaseline_followup_final_analysis%>%
  dplyr::select(study_id, wdf_q1_9, wdf_q1_5, wdf_q1_4_age_group,
                #History of medical conditions and treatment
    wdf_q2_1, wdf_q2_9, wdf_q2_19a:wdf_q2_19f,
    #Lifestyle history/Health behaviour
    wdf_q3_2, wdf_q3_7, wdf_q3_10, wdf_q3_14,
    #Clinical and anthropometric measurements
    wdf_q5_0a:wdf_q5_0c, wdf_q5_8a, wdf_q5_8b, wdf_q5_10, wdf_q5_1_2_3a, wdf_q5_1_2_3b, wdf_q5_6_7, 
    wdf_q5_5_6_7_bmi, wdf_q5_8a_b_waist_hip_ratio)%>%
  drop_na()%>%
  group_by(study_id)%>%
  filter(n()==2)%>%
  ungroup()%>%
  pivot_longer(
    cols = c(wdf_q5_8a, wdf_q5_8b, wdf_q5_10, wdf_q5_1_2_3a, wdf_q5_1_2_3b, wdf_q5_6_7, 
    wdf_q5_5_6_7_bmi, wdf_q5_8a_b_waist_hip_ratio),
    names_to = "clinical_parameters",
    values_to = "value"
  )%>%
  mutate(clinical_parameters = as_factor(clinical_parameters))%>%
  nest_by(clinical_parameters)%>%
  mutate(lmm_random_intercept_model = list(lmer(value ~ wdf_q1_5 + wdf_q1_4_age_group + wdf_q2_1 +wdf_q2_9 + wdf_q2_19a + 
        wdf_q2_19b + wdf_q2_19c + wdf_q2_19d + wdf_q2_19e + wdf_q2_19f + wdf_q3_2 + wdf_q3_7 + wdf_q3_10 + wdf_q3_14 + 
          wdf_q5_0a + wdf_q5_0b + wdf_q5_0c + wdf_q1_9 + (1 | study_id), data = data, REML = TRUE)),
         lmm_random_intercept_null_model = list(lmer(value ~ 1 + (1 | study_id), data = data, REML = TRUE)),
        table_out_random_intercept = list(tbl_regression(lmm_random_intercept_model, exponentiate = FALSE, #broom.mixed package required
    estimate_fun = ~style_sigfig(.x, digits = 2),
    pvalue_fun = ~style_pvalue(.x, digits = 3))%>%
  #add_global_p()%>% # add global p-value for categorical variables
  bold_p(t= 0.05) %>% # bold p-values under a given threshold (default 0.05)
  bold_labels() %>%
  italicize_levels()%>% 
  modify_header(label = "**Linear Mixed full Model - random_intercept**")%>% # update the column header
  add_significance_stars(
    pattern = "{estimate} ({conf.low} to {conf.high}){stars}",
    hide_ci = TRUE, hide_se = TRUE , hide_p = FALSE) %>%
  modify_header(estimate ~ "**Beta (95% CI)**") %>%
  modify_footnote(estimate ~ "Beta, CI = Confidence Interval", abbreviation = TRUE)
    )
  )

tbl_merge(diabetes_mixed_model$table_out_random_intercept,
    tab_spanner = c("**Systolic Blood pressure**", "**Diastolic Blood pressure**", "**Blood glucose (mmol/L)**", "**BMI (kg/m2)**",
                    "**Weight in kgs**", "**Waist circumference**", "**Waist-to-hip ratio**", "**Hip circumference**"))

```

### Linear mixed model metrics

```{r mixed model metrics}

diabetes_random_intercept_model_metrics <- list()

diabetes_random_intercept_null_model_metrics <- list()

diabetes_mixed_model_comparison <- list()

for (i in 1:length(diabetes_mixed_model$clinical_parameters)){
  
  diabetes_random_intercept_model_metrics[i] <- print(
    kable(
    list(broom::glance(diabetes_mixed_model$lmm_random_intercept_model[[i]])),
    caption = paste0("full model",diabetes_mixed_model$clinical_parameters[[i]]) )
  )
  
  diabetes_random_intercept_null_model_metrics[i] <- print(
    kable(
    list(broom::glance(diabetes_mixed_model$lmm_random_intercept_null_model[[i]])),
    caption = paste0("null model", diabetes_mixed_model$clinical_parameters[[i]]) )
  
  )
  
  diabetes_mixed_model_comparison[i] <- print(
    kable(
    list(anova(diabetes_mixed_model$lmm_random_intercept_null_model[[i]], diabetes_mixed_model$lmm_random_intercept_model[[i]])),
    caption = paste0("null model-full model", diabetes_mixed_model$clinical_parameters[[i]]) )
  
  )
  
}


```


## Change in score - linear regression

```{r Change in score linear regression model}

diabetes_change_in_score_model <- diabetes_baseline_final_clean%>%
  dplyr::select(study_id, wdf_q1_9, wdf_q1_5, wdf_q1_4_age_group,
                #History of medical conditions and treatment
    wdf_q2_1, wdf_q2_9, wdf_q2_19a:wdf_q2_19f,
    #Lifestyle history/Health behaviour
    wdf_q3_2, wdf_q3_7, wdf_q3_10, wdf_q3_14,
    #Clinical and anthropometric measurements
    wdf_q5_0a:wdf_q5_0c, wdf_q5_8a, wdf_q5_8b, wdf_q5_10, wdf_q5_1_2_3a, wdf_q5_1_2_3b, wdf_q5_6_7, 
    wdf_q5_5_6_7_bmi, wdf_q5_8a_b_waist_hip_ratio)%>%
  left_join(diabetes_followup_final_clean%>%
              filter(wdf_q1_9_followup == "Six month follow-up")%>%
              dplyr::select(study_id, wdf_q5_8a_followup, wdf_q5_8b_followup, wdf_q5_10_followup, wdf_q5_1_2_3a_followup,
                            wdf_q5_1_2_3b_followup, wdf_q5_6_7_followup, wdf_q5_5_6_7_followup_bmi, wdf_q5_8a_b_followup_waist_hip_ratio),
            by = c("study_id" = "study_id"))%>%
    mutate(across(c(wdf_q2_1, wdf_q2_9, wdf_q3_2, wdf_q3_7, wdf_q3_10, wdf_q3_14, wdf_q5_0a:wdf_q5_0c), ~fct_rev(.x)),
         across(c(wdf_q2_19a:wdf_q2_19f), ~factor(.x, levels = c("No", "Yes", "Dont Know"))),
         change_wdf_q5_8a = wdf_q5_8a_followup - wdf_q5_8a,
         change_wdf_q5_8b = wdf_q5_8b_followup - wdf_q5_8b,
         change_wdf_q5_10 = wdf_q5_10_followup - wdf_q5_10,
         change_wdf_q5_1_2_3a = wdf_q5_1_2_3a_followup - wdf_q5_1_2_3a,
         change_wdf_q5_1_2_3b = wdf_q5_1_2_3b_followup - wdf_q5_1_2_3b,
         change_wdf_q5_6_7 = wdf_q5_6_7_followup - wdf_q5_6_7,
         change_wdf_q5_5_6_7_bmi = wdf_q5_5_6_7_followup_bmi - wdf_q5_5_6_7_bmi,
         change_wdf_q5_8a_b_waist_hip_ratio = wdf_q5_8a_b_followup_waist_hip_ratio - wdf_q5_8a_b_waist_hip_ratio
         )%>%
  dplyr::select(-c(wdf_q5_8a, wdf_q5_8b, wdf_q5_10, wdf_q5_1_2_3a, wdf_q5_1_2_3b, wdf_q5_6_7, 
    wdf_q5_5_6_7_bmi, wdf_q5_8a_b_waist_hip_ratio, wdf_q5_8a_followup, wdf_q5_8b_followup, wdf_q5_10_followup, wdf_q5_1_2_3a_followup,
                            wdf_q5_1_2_3b_followup, wdf_q5_6_7_followup, wdf_q5_5_6_7_followup_bmi, wdf_q5_8a_b_followup_waist_hip_ratio))%>%
  labelled::set_variable_labels(!!!diabetes_baseline_followup_labels[names(diabetes_baseline_followup_labels) %in% names(.)])%>% #labeling variables from data dictionary
  drop_na()%>%
  pivot_longer(
    cols = c(change_wdf_q5_8a, change_wdf_q5_8b, change_wdf_q5_10, change_wdf_q5_1_2_3a, change_wdf_q5_1_2_3b, change_wdf_q5_6_7,
             change_wdf_q5_5_6_7_bmi, change_wdf_q5_8a_b_waist_hip_ratio),
    names_to = "clinical_parameters",
    values_to = "value"
  )%>%
  mutate(clinical_parameters = as_factor(clinical_parameters))%>%
  nest_by(clinical_parameters)%>%
  mutate(lm_model = list(glm(value ~ wdf_q1_5 + wdf_q1_4_age_group + wdf_q2_1 +wdf_q2_9 + wdf_q2_19a + 
        wdf_q2_19b + wdf_q2_19c + wdf_q2_19d + wdf_q2_19e + wdf_q2_19f + wdf_q3_2 + wdf_q3_7 + wdf_q3_10 + wdf_q3_14 + 
          wdf_q5_0a + wdf_q5_0b + wdf_q5_0c , data = data, family = gaussian  )),
        lm_null_model = list(glm(value ~ 1 , data = data, family = gaussian  )),
        table_out_lm = list(tbl_regression(lm_model, exponentiate = FALSE, #broom.mixed package required
    estimate_fun = ~style_sigfig(.x, digits = 2),
    pvalue_fun = ~style_pvalue(.x, digits = 3))%>%
  #add_global_p()%>% # add global p-value for categorical variables
  bold_p(t= 0.05) %>% # bold p-values under a given threshold (default 0.05)
  bold_labels() %>%
  italicize_levels()%>% 
  modify_header(label = "**Linear regression**")%>% # update the column header
  add_significance_stars(
    pattern = "{estimate} ({conf.low} to {conf.high}){stars}",
    hide_ci = TRUE, hide_se = TRUE , hide_p = FALSE) %>%
  modify_header(estimate ~ "**Beta (95% CI)**") %>%
  modify_footnote(estimate ~ "Beta, CI = Confidence Interval", abbreviation = TRUE)
    )
  )


tbl_merge(diabetes_change_in_score_model$table_out_lm,
    tab_spanner = c("**Systolic Blood pressure**", "**Diastolic Blood pressure**", "**Blood glucose (mmol/L)**", "**BMI (kg/m2)**",
                    "**Weight in kgs**", "**Waist circumference**", "**Waist-to-hip ratio**", "**Hip circumference**"))

```


### change in score - linear regression model metrics

```{r Change in score linear regression model metrics}

diabetes_change_in_score_model_metrics <- list()

diabetes_change_in_score_null_model_metrics <- list()

diabetes_change_in_score_model_comparison <- list()

for (i in 1:length(diabetes_change_in_score_model$clinical_parameters)){
  
  diabetes_change_in_score_model_metrics[i] <- print(
    kable(
    list(broom::glance(diabetes_change_in_score_model$lm_model[[i]])),
    caption = paste0("full model",diabetes_change_in_score_model$clinical_parameters[[i]]) )
  )
  
  diabetes_change_in_score_null_model_metrics[i] <- print(
    kable(
    list(broom::glance(diabetes_change_in_score_model$lm_null_model[[i]])),
    caption = paste0("null model", diabetes_change_in_score_model$clinical_parameters[[i]]) )
  
  )
  
  diabetes_change_in_score_model_comparison[i] <- print(
    kable(
    list(anova(diabetes_change_in_score_model$lm_null_model[[i]], diabetes_change_in_score_model$lm_model[[i]])),
    caption = paste0("null model-full model", diabetes_change_in_score_model$clinical_parameters[[i]]) )
  )
  
}


```
















