---
title: "Diabetes WDF followup"
author: "Reinpeter"
date: "`r Sys.Date()`"
output:
  word_document: 
    fig_width: 12
    fig_height: 8
    number_sections: yes
  pdf_document:
    fig_width: 12
    fig_height: 8
    number_sections: yes
  html_document:
    toc: yes
    toc_depth: 4
    number_sections: yes
---



```{r setup, results="hide", include=FALSE}

## Set Chunk requirements
knitr::opts_chunk$set(#include = TRUE,
                      echo=FALSE, message = FALSE, warning = FALSE)

```

```{r setting working directory, include=FALSE, results = "hide"}

## Setting work directory

setwd(".")


```

```{r loading relevant packages, include=FALSE, results = "hide"}

#library we need
libs_diabetes_followup <- c("googledrive" ,"tidyverse", "haven", "janitor", "knitr",
                            "lubridate", "plotly", "gtsummary", "flextable")

#install missing libraries

inatalled_libs_diabetes_followup <- libs_diabetes_followup  %in% rownames(installed.packages())
if (any(inatalled_libs_diabetes_followup==F)) {
  install.packages(libs_diabetes_followup[!inatalled_libs_diabetes_followup])
}

#load libraries

invisible(lapply(libs_diabetes_followup, library, character.only=T))


set_gtsummary_theme(list(
  "tbl_summary-fn:percent_fun" = function(x) style_percent(x, digits = 1),
  "tbl_summary-str:categorical_stat" = "{n} ({p}%)"
))
# Setting `Compact` theme
theme_gtsummary_compact()

```


```{r googledrive downloading diabetes data, results="hide", include=FALSE}

 drive_auth(#email = "guest360@aphrc.org"
           )

  #drive_user()

  diabetes_followup_file_id <- drive_find(shared_drive = c(shared_drive_find(pattern = "Data Science Programs")$id),
           q = c("name contains 'wdffollowup_cleaned.dta'")) #search for a specific set of shared drives, use the query string q

  
  diabetes_followup_local_download <- drive_download(diabetes_followup_file_id$id, overwrite = TRUE)


```


```{r reading diabetes data locally, results="hide", include=FALSE}

  ##Reading the .dta with labelled vector converted to a factor

  diabetes_followup <- read_dta("wdffollowup_cleaned.dta")%>%
  mutate_if(haven::is.labelled, as_factor)%>%
  rename_with(~paste0(.x,"_followup"))%>%
   labelled::set_variable_labels( #relabeling specific variables
     wdf_q2_3a_followup = "For how long have you had diabetes, since you were diagnosed (units-D, W, M, Y)?",
     wdf_q2_3b_followup = "For how long have you had diabetes, since you were diagnosed (# of units)?",
     wdf_q2_11a_followup = "How long have you had high BP, since you were diagnosed (units-D, W, M, Y)?",
     wdf_q2_11b_followup = "How long have you had high BP, since you were diagnosed (# of units)?",
     wdf_q2_15a_followup = "Medication you were taking to treat the Hypertension? - Tablets prescribed by a health worker",
     wdf_q2_15b_followup = "Medication you were taking to treat the Hypertension? - Tablets i got from a drug store without a prescription",
     wdf_q2_15c_followup = "Medication you were taking to treat the Hypertension? - Tablets i got from relatives/friends w/o prescription",
     wdf_q2_15d_followup = "Medication you were taking to treat the Hypertension? - Herbal medicine together with tabs",
     wdf_q2_15e_followup = "Medication you were taking to treat the Hypertension? - Herbal medicine only",
     wdf_q2_15f_followup = "Medication you were taking to treat the Hypertension? - Other",
     wdf_q2_16a_followup = "Where were you getting treatment for High BP before you started attending this clinic? - Kenyatta national hospital",
     wdf_q2_16b_followup = "Where were you getting treatment for High BP before you started attending this clinic? - Govt district hospital",
     wdf_q2_16c_followup = "Where were you getting treatment for High BP before you started attending this clinic? - Govt health centre",
     wdf_q2_16d_followup = "Where were you getting treatment for High BP before you started attending this clinic? - Private hospital",
     wdf_q2_16e_followup = "Where were you getting treatment for High BP before you started attending this clinic? - Other hospital",
     wdf_q2_16f_followup = "Where were you getting treatment for High BP before you started attending this clinic? - Other health facility",
     wdf_q2_16g_followup = "Where were you getting treatment for High BP before you started attending this clinic? - I started treatment from here",
     wdf_q2_16h_followup = "Where were you getting treatment for High BP before you started attending this clinic? - I don't remember",
     wdf_q2_16i_followup = "Where were you getting treatment for High BP before you started attending this clinic? - Other",
     wdf_q2_19a_followup = "Have peripheral neuropathy complication",
     wdf_q2_19b_followup = "Have poor vision complication",
     wdf_q2_19d_followup = "Have kidney problems complication",
     wdf_q2_19e_followup = "Have chest pain complication",
     wdf_q2_19f_followup = "Have body swelling (abdominal or pedal oedema) complication",
     wdf_q3_1_followup = "Have you smoked tobacco in the last 6/12 months?",
     wdf_q3_10_followup = "Have you consumed alcohol within the past 6/12 months?",
     wdf_q3_32_followup = "In the last six/twelve months, have you changed anything about your fruit consumption?",
     wdf_q3_34_followup = "In the last six/twelve months, have you changed anything about your vegetable consumption?",
     wdf_q3_36_followup = "In the last six/twelve months, have you changed anything about your salt consumption?",
     wdf_q3_38_followup = "In the last six/twelve months, have you changed anything about your red meat consumption?",
     wdf_q3_40_followup = "In the last six/twelve months, have you changed anything about your sugar consumption?",
     wdf_q3_42_followup = "In the last six/twelve months, have you changed anything about your water consumption?",
     wdf_q3_44_followup = "In the last six/twelve months, have you changed anything else about your eating or drinking habits?",
     wdf_q3_46_followup = "In the last six/twelve months, have you changed anything about your physical activity, say in the way you travel to and from places,the kind of work you do or the way you spend your leisure time?",
     wdf_q5_3a_followup = "Blood pressure today-Systolic",
     wdf_q5_3b_followup = "Blood pressure today-Diastolic",
     wdf_q5_10_followup = "Blood glucose (mmol/L)",
     wdf_q5_11_followup = "Hba1c measurement (%)"
     )
  
  diabetes_followup1 <- read_dta("wdffollowup_cleaned.dta")
  

  diabetes_followup_six <- read_dta("wdffollowup_cleaned.dta")%>%
  mutate_if(is.labelled, as_factor)%>%
  filter(wdf_q1_9 == "Six month follow-up")
  
  diabetes_followup_six1 <- read_dta("wdffollowup_cleaned.dta")%>% 
  filter(wdf_q1_9 == 1)
  
  diabetes_followup_twelve <- read_dta("wdffollowup_cleaned.dta")%>%
  mutate_if(is.labelled, as_factor)%>%
  filter(wdf_q1_9 == "One year follow-up")
  
  diabetes_followup_twelve1 <- read_dta("wdffollowup_cleaned.dta")%>% 
  filter(wdf_q1_9 == 2)
  
 
  diabetes_followup_variable_attr <- as.data.frame(labelled::generate_dictionary(diabetes_followup))

  diabetes_followup_variable_attr1 <- as.data.frame(labelled::look_for(diabetes_followup1, labels = TRUE, values = TRUE))

```

```{r assigning variable labels}

#Creating a named vector to quickly assign the variable labels

diabetes_followup_labels <- diabetes_followup_variable_attr%>%
  select(variable, label)%>%
  deframe()

```


```{r saving data localy, results="hide", include=FALSE}

#saving as .csv

readr::write_csv(diabetes_followup_six,"wdffollowup_cleaned_six_months.csv", na="")

readr::write_csv(diabetes_followup_twelve,"wdffollowup_cleaned_twelve_months.csv", na="")


```


```{r reading scan report, results="hide", include=FALSE}

#downloading data from shared google drive

scan_report_followup_six_id <- drive_find(shared_drive = c(shared_drive_find(pattern = "Data Science Programs")$id),
           q = c("name contains 'ScanReport_wdffollowup_six_months.xlsx'")) #search for a specific set of shared drives, use the query string q

scan_report_followup_twelve_id <- drive_find(shared_drive = c(shared_drive_find(pattern = "Data Science Programs")$id),
           q = c("name contains 'ScanReport_wdffollowup_twelve_months.xlsx'")) #search for a specific set of shared drives, use the query string q


scan_report_followup_six_local_download <- drive_download(scan_report_followup_six_id$id, overwrite = TRUE)


scan_report_followup_twelve_local_download <- drive_download(scan_report_followup_twelve_id$id, overwrite = TRUE)


```


```{r importing saved baselineRdata files, results="hide", include=FALSE}

#load .Rdata files

wdfbaseline_clean_final_list <- list.files(path = ".", pattern = "wdfbaseline_cleaned_final.RData", full.names = TRUE)

#baseline data for filling and duplicating specific columns in followup data

invisible(lapply(wdfbaseline_clean_final_list, load, .GlobalEnv))

```


```{r creating unique id, results="hide", include=FALSE}

#creating unique id from names of participants from baseline and followup data

unique_id <- rbind(diabetes_baseline_final_clean%>%dplyr::select(wdf_q1_6, wdf_q1_4),
                   data.table::setnames(diabetes_followup%>%dplyr::select(wdf_q1_6_followup, wdf_q1_4_followup),
                                        names(diabetes_baseline_final_clean%>%dplyr::select(wdf_q1_6, wdf_q1_4))
                   ))%>%
  distinct(wdf_q1_6, wdf_q1_4)%>%
  mutate(study_id = 1:n())%>%
  labelled::set_variable_labels( #relabeling specific variables
    study_id = "Created respondent id"
  )


```


```{r final data, results="hide", include=FALSE}

diabetes_followup_final <- diabetes_followup%>%
  left_join(unique_id, 
            by = c("wdf_q1_6_followup" = "wdf_q1_6", "wdf_q1_4_followup" = "wdf_q1_4"))%>%
  dplyr::select(study_id, wdf_q1_2_followup:wdf_q5_11_followup)%>%
  left_join(diabetes_baseline_final_clean%>%
              dplyr::select(wdf_q1_6, wdf_q1_4, wdf_q2_2, wdf_q2_4, wdf_q2_5:wdf_q2_8isp, wdf_q2_10, wdf_q2_12, wdf_q2_13, wdf_q2_14,
                            wdf_q2_15a, wdf_q2_15b, wdf_q2_15c, wdf_q2_15d, wdf_q2_15e, wdf_q2_15f, wdf_q2_16a, wdf_q2_16b, 
                            wdf_q2_16c, wdf_q2_16d, wdf_q2_16e, wdf_q2_16f, wdf_q2_16g, wdf_q2_16h, wdf_q2_16i, wdf_q2_17a, wdf_q2_18a,
                            wdf_q3_4, wdf_q3_9, wdf_q3_15,
                            wdf_q5_5a, wdf_q5_5b), 
            by = c("wdf_q1_6_followup" = "wdf_q1_6", "wdf_q1_4_followup" = "wdf_q1_4"))%>%
  mutate(wdf_q2_2_followup = wdf_q2_2, #Filling column with baseline data
         wdf_q2_3b_followup = round(time_length(interval(wdf_q2_2_followup, wdf_q1_2_followup),
                                                unit = "year"),2), #calculate time length in years, months, weeks, days
         wdf_q2_3a_followup = if_else(wdf_q2_3b_followup<1, "Months", "Years"),
          wdf_q2_3b_followup = if_else(wdf_q2_3b_followup == 0.54, 6.48,
                                      if_else(wdf_q2_3b_followup == 0.73, 8.76, 
                                      if_else(wdf_q2_3b_followup == 0.78, 9.36, 
                                      if_else(wdf_q2_3b_followup == 0.84, 10.08,
                                      if_else(wdf_q2_3b_followup == 0.90, 10.80,
                                      if_else(wdf_q2_3b_followup == 0.96, 11.52, wdf_q2_3b_followup)))))),
         wdf_q2_4_followup = wdf_q2_4, #Filling column with baseline data
         wdf_q2_10_followup = if_else(wdf_q2_9_followup == "Yes" & is.na(wdf_q2_10_followup), wdf_q2_10,
                                      wdf_q2_10_followup), #Filling column with baseline data
         wdf_q2_11b_followup = if_else(is.na(wdf_q2_11b_followup), round(time_length(interval(wdf_q2_10_followup, wdf_q1_2_followup),
                                                unit = "year"),2) , wdf_q2_11b_followup), #calculate time length in years, months, weeks, days
         wdf_q2_11a_followup = if_else(is.na(wdf_q2_11a_followup) & wdf_q2_11b_followup<1, "Months",
                               if_else(is.na(wdf_q2_11a_followup) & wdf_q2_11b_followup>= 1, "Years", wdf_q2_11a_followup)),
         wdf_q2_11b_followup = if_else(wdf_q2_11b_followup == 0.81, 9.72,
                                      if_else(wdf_q2_11b_followup == 0.88, 10.56, 
                                      if_else(wdf_q2_11b_followup == 0.92, 11.04, 
                                      if_else(wdf_q2_11b_followup == 0.96, 11.52, wdf_q2_11b_followup)))),
    across(c(wdf_q2_3a_followup, wdf_q2_11a_followup), ~ factor(.x, levels = c("Days", "Weeks", "Months", "Years"))), #columns to factor
    across(c(wdf_q2_3b_followup, wdf_q2_11b_followup ), ~ round(.x, 0)), #round column values 
         wdf_q2_12_followup = if_else(wdf_q2_9_followup == "No", NA,
                              if_else(is.na(wdf_q2_12_followup), wdf_q2_12, wdf_q2_12_followup)), #Filling column with baseline data
    wdf_q2_13_followup = if_else(is.na(wdf_q2_13_followup), wdf_q2_13, wdf_q2_13_followup), #Filling column with baseline data
    wdf_q2_14_followup = if_else(is.na(wdf_q2_14_followup), wdf_q2_14, wdf_q2_14_followup), #Filling column with baseline data
    wdf_q2_15a_followup = if_else(is.na(wdf_q2_15a_followup), wdf_q2_15a, wdf_q2_15a_followup), #Filling column with baseline data
    wdf_q2_15b_followup = if_else(is.na(wdf_q2_15b_followup), wdf_q2_15b, wdf_q2_15b_followup), #Filling column with baseline data
    wdf_q2_15c_followup = if_else(is.na(wdf_q2_15c_followup), wdf_q2_15c, wdf_q2_15c_followup), #Filling column with baseline data
    wdf_q2_15d_followup = if_else(is.na(wdf_q2_15d_followup), wdf_q2_15d, wdf_q2_15d_followup), #Filling column with baseline data
    wdf_q2_15e_followup = if_else(is.na(wdf_q2_15e_followup), wdf_q2_15e, wdf_q2_15e_followup), #Filling column with baseline data
    wdf_q2_15f_followup = if_else(is.na(wdf_q2_15f_followup), wdf_q2_15f, wdf_q2_15f_followup), #Filling column with baseline data
    wdf_q2_16a_followup = if_else(is.na(wdf_q2_16a_followup), wdf_q2_16a, wdf_q2_16a_followup), #Filling column with baseline data
    wdf_q2_16b_followup = if_else(is.na(wdf_q2_16b_followup), wdf_q2_16b, wdf_q2_16b_followup), #Filling column with baseline data
    wdf_q2_16c_followup = if_else(is.na(wdf_q2_16c_followup), wdf_q2_16c, wdf_q2_16c_followup), #Filling column with baseline data
    wdf_q2_16d_followup = if_else(is.na(wdf_q2_16d_followup), wdf_q2_16d, wdf_q2_16d_followup), #Filling column with baseline data
    wdf_q2_16e_followup = if_else(is.na(wdf_q2_16e_followup), wdf_q2_16e, wdf_q2_16e_followup), #Filling column with baseline data
    wdf_q2_16f_followup = if_else(is.na(wdf_q2_16f_followup), wdf_q2_16f, wdf_q2_16f_followup), #Filling column with baseline data
    wdf_q2_16g_followup = if_else(is.na(wdf_q2_16g_followup), wdf_q2_16g, wdf_q2_16g_followup), #Filling column with baseline data
    wdf_q2_16h_followup = if_else(is.na(wdf_q2_16h_followup), wdf_q2_16h, wdf_q2_16h_followup), #Filling column with baseline data
    wdf_q2_16i_followup = if_else(is.na(wdf_q2_16i_followup), wdf_q2_16i, wdf_q2_16i_followup), #Filling column with baseline data
    wdf_q3_17a_followup = ifelse(is.na(wdf_q3_17a_followup) | wdf_q3_17a_followup == 2, "No", wdf_q3_17a_followup), #Replace NA to No
    across(c(wdf_q3_2_followup, wdf_q3_3_followup, wdf_q3_7_followup, wdf_q3_8_followup, wdf_q3_14_followup, 
             wdf_q3_17b_followup:wdf_q3_17g_followup, wdf_q3_33a_followup:wdf_q3_33g_followup, wdf_q3_35a_followup:wdf_q3_35g_followup,
             wdf_q3_37a_followup:wdf_q3_37g_followup, wdf_q3_39a_followup:wdf_q3_39f_followup, wdf_q3_41a_followup:wdf_q3_41h_followup,
             wdf_q3_43a_followup:wdf_q3_43g_followup, wdf_q3_45a_followup:wdf_q3_45k_followup,
             wdf_q3_47a_followup:wdf_q3_47i_followup), ~ as.character(.x)), #columns to character
    across(c(wdf_q3_2_followup, wdf_q3_3_followup, wdf_q3_7_followup, wdf_q3_8_followup, wdf_q3_14_followup,
             wdf_q3_17b_followup:wdf_q3_17g_followup, wdf_q3_33a_followup:wdf_q3_33g_followup, wdf_q3_35a_followup:wdf_q3_35g_followup,
             wdf_q3_37a_followup:wdf_q3_37g_followup, wdf_q3_39a_followup:wdf_q3_39f_followup, wdf_q3_41a_followup:wdf_q3_41h_followup,
             wdf_q3_43a_followup:wdf_q3_43g_followup, wdf_q3_45a_followup:wdf_q3_45k_followup,
             wdf_q3_47a_followup:wdf_q3_47i_followup), ~ ifelse(is.na(.x), "No", .x)), #Replace NA to No
    across(c(wdf_q3_2_followup, wdf_q3_3_followup, wdf_q3_7_followup, wdf_q3_8_followup, wdf_q3_14_followup, wdf_q3_17a_followup,
             wdf_q3_17b_followup:wdf_q3_17g_followup, wdf_q3_33a_followup:wdf_q3_33g_followup, wdf_q3_35a_followup:wdf_q3_35g_followup,
             wdf_q3_37a_followup:wdf_q3_37g_followup, wdf_q3_39a_followup:wdf_q3_39f_followup, wdf_q3_41a_followup:wdf_q3_41h_followup,
             wdf_q3_43a_followup:wdf_q3_43g_followup, wdf_q3_45a_followup:wdf_q3_45k_followup,
             wdf_q3_47a_followup:wdf_q3_47i_followup), ~ factor(.x, levels = c("Yes", "No")) ), #Column to Factor
    wdf_q5_5a_followup = wdf_q5_5a, #duplicating 1st reading height from baseline data
    wdf_q5_5b_followup =  wdf_q5_5b, #duplicating 2nd reading height from baseline data
    wdf_q2_5_followup = wdf_q2_5, #duplicating from baseline data
    wdf_q2_6_followup = wdf_q2_6, #duplicating from baseline data
    wdf_q2_7a_followup = wdf_q2_7a, #duplicating from baseline data
    wdf_q2_7b_followup = wdf_q2_7b, #duplicating from baseline data
    wdf_q2_7c_followup = wdf_q2_7c, #duplicating from baseline data
    wdf_q2_7d_followup = wdf_q2_7d, #duplicating from baseline data
    wdf_q2_7e_followup = wdf_q2_7e, #duplicating from baseline data
    wdf_q2_7f_followup = wdf_q2_7f, #duplicating from baseline data
    wdf_q2_7g_followup = wdf_q2_7g, #duplicating from baseline data
    wdf_q2_7sp_followup = wdf_q2_7sp, #duplicating from baseline data
    wdf_q2_8a_followup = wdf_q2_8a, #duplicating from baseline data
    wdf_q2_8b_followup = wdf_q2_8b, #duplicating from baseline data
    wdf_q2_8bsp_followup = wdf_q2_8bsp, #duplicating from baseline data
    wdf_q2_8c_followup = wdf_q2_8c, #duplicating from baseline data
    wdf_q2_8csp_followup = wdf_q2_8csp, #duplicating from baseline data
    wdf_q2_8d_followup = wdf_q2_8d, #duplicating from baseline data
    wdf_q2_8dsp_followup = wdf_q2_8dsp, #duplicating from baseline data
    wdf_q2_8e_followup = wdf_q2_8e, #duplicating from baseline data
    wdf_q2_8esp_followup = wdf_q2_8esp, #duplicating from baseline data
    wdf_q2_8f_followup = wdf_q2_8f, #duplicating from baseline data
    wdf_q2_8fsp_followup = wdf_q2_8fsp, #duplicating from baseline data
    wdf_q2_8g_followup = wdf_q2_8g, #duplicating from baseline data
    wdf_q2_8h_followup = wdf_q2_8h, #duplicating from baseline data
    wdf_q2_8i_followup = wdf_q2_8i, #duplicating from baseline data
    wdf_q2_8isp_followup = wdf_q2_8isp, #duplicating from baseline data
    wdf_q2_17a_followup = wdf_q2_17a, #duplicating from baseline data
    wdf_q2_18a_followup = wdf_q2_18a, #duplicating from baseline data
    wdf_q3_4_followup = wdf_q3_4, #duplicating from baseline data
    wdf_q3_9_followup = wdf_q3_9, #duplicating from baseline data
    wdf_q3_15_followup = wdf_q3_15 #duplicating from baseline data
    )%>%
  labelled::set_variable_labels(!!!diabetes_followup_labels[names(diabetes_followup_labels) %in% names(.)])%>% #labeling variables from data dictionary 
  mutate_if(is.factor, ~fct_drop(.x #, only = c("")
            )) #drop unused factor levels
  
```


```{r final clean data, results="hide", include=FALSE}

diabetes_followup_final_clean <- diabetes_followup_final%>%
  dplyr::select(study_id, wdf_q1_2_followup:wdf_q5_11_followup, wdf_q5_5a_followup:wdf_q3_15_followup)%>%
  mutate(wdf_q1_4_followup_age = round(time_length(difftime(wdf_q1_2_followup, wdf_q1_4_followup, units = "auto"),
                                                   unit = "year"),2), #creating age column
          wdf_q1_4_followup_age_group = ifelse(wdf_q1_4_followup_age < 51, "50 and below",
                          ifelse(wdf_q1_4_followup_age  < 61, "51-60 years", "61 years and above" )), #creating age group column
          wdf_q1_4_followup_age_group = factor(wdf_q1_4_followup_age_group,
                                               levels = c("50 and below", "51-60 years", "61 years and above")), #factor age group column
         wdf_q2_3a_b_followup_years = round(time_length(as.period(str_to_lower(wdf_q2_3a_followup))*(as.numeric(wdf_q2_3b_followup)),
                                                        unit = "year"),3), #creating duration of diabetes in years column
          wdf_q2_3a_b_followup_years_group = ifelse(wdf_q2_3a_b_followup_years < 5, "Below 5 years",
                ifelse(wdf_q2_3a_b_followup_years  < 10, "5-9 years", "10 years and above" )), #creating duration of diabetes in years group column
          wdf_q2_3a_b_followup_years_group = factor(wdf_q2_3a_b_followup_years_group, 
                            levels = c("Below 5 years", "5-9 years", "10 years and above")), #factor duration of diabetes in years group column
         wdf_q2_11a_b_followup_years = round(time_length(as.period(str_to_lower(wdf_q2_11a_followup))*(as.numeric(wdf_q2_11b_followup)),
                                                         unit = "year"),3), #creating duration of hypertension in years column
          wdf_q2_11a_b_followup_years_group = ifelse(wdf_q2_11a_b_followup_years < 5, "Below 5 years",
            ifelse(wdf_q2_11a_b_followup_years  < 10, "5-9 years", "10 years and above" )), #creating duration of hypertension in years group column
          wdf_q2_11a_b_followup_years_group = factor(wdf_q2_11a_b_followup_years_group, levels = c("Below 5 years", "5-9 years", "10 years and above")), #factor duration of hypertension in years group column
          wdf_q5_1_2_3a_followup = round(rowMeans(across(c(wdf_q5_1a_followup,wdf_q5_2a_followup,wdf_q5_3a_followup)),
                                                  na.rm = TRUE),0), #creating average Systolic BP column
          wdf_q5_1_2_3b_followup = round(rowMeans(across(c(wdf_q5_1b_followup,wdf_q5_2b_followup,wdf_q5_3b_followup)),
                                                  na.rm = TRUE),0), #creating average Diastolic BP column
          wdf_q5_followup_bp = ifelse(wdf_q5_1_2_3a_followup <120 & wdf_q5_1_2_3b_followup <80,
                                      "< 120/80", ">=120/80"), #Creating < 120/80 & >=120/80 BP group column
          wdf_q5_followup_bp = factor(wdf_q5_followup_bp, levels = c("< 120/80", ">=120/80")), #factor < 120/80 & >=120/80 BP group column
          wdf_q5_5a_b_followup = round(rowMeans(across(c(wdf_q5_5a_followup, wdf_q5_5b_followup)),
                                                na.rm = TRUE)/100,2), #creating average height in meters column
          wdf_q5_6_7_followup = round(rowMeans(across(c(wdf_q5_61_followup, wdf_q5_7_followup)),
                                               na.rm = TRUE),1), #creating average weight in meters column
          wdf_q5_5_6_7_followup_bmi = round(wdf_q5_6_7_followup/((wdf_q5_5a_b_followup)^2),2), #creating BMI column
          wdf_q5_5_6_7_followup_bmi_group = ifelse(wdf_q5_5_6_7_followup_bmi <18.5, "Underweight (<18.5)",
                                    ifelse(wdf_q5_5_6_7_followup_bmi <25, "Normal (18.5–24.9)",
                                    ifelse(wdf_q5_5_6_7_followup_bmi <30, "Overweight (25–29.9)", "Obese (>=30)"))), #Creating BMI group column
          wdf_q5_5_6_7_followup_bmi_group = factor(wdf_q5_5_6_7_followup_bmi_group, levels = c("Underweight (<18.5)", "Normal (18.5–24.9)",
                                                    "Overweight (25–29.9)", "Obese (>=30)")), #factor BMI group column
          wdf_q5_8a_b_followup_waist_hip_ratio = round(wdf_q5_8a_followup/wdf_q5_8b_followup,2), #creating waist hip ratio column
          wdf_q5_8a_b_followup_waist_hip_ratio_group = 
                  ifelse(wdf_q1_5_followup == "Female" & wdf_q5_8a_b_followup_waist_hip_ratio < 0.87, "Normal (Male <=0.95; Female <=0.86)",
                    ifelse(wdf_q1_5_followup == "Male" & wdf_q5_8a_b_followup_waist_hip_ratio < 0.96, "Normal (Male <=0.95; Female <=0.86)",
                                                     "At Risk (Male >0.95; Female >0.86)")), #creating waist hip ratio group column
          wdf_q5_8a_b_followup_waist_hip_ratio_group = factor(wdf_q5_8a_b_followup_waist_hip_ratio_group,
                                        levels = c("Normal (Male <=0.95; Female <=0.86)", "At Risk (Male >0.95; Female >0.86)")), #factor waist hip ratio group column
          wdf_q5_10_followup_group = ifelse(wdf_q5_10_followup <8.2, "Less than 8.2",
                                            "8.2 and higher"), #Creating <8.2 & >=8.2 blood glucose group column
          wdf_q5_10_followup_group = factor(wdf_q5_10_followup_group,
                                            levels = c("Less than 8.2", "8.2 and higher")), #factor <8.2 & >=8.2 blood glucose group column
  )%>%
   labelled::set_variable_labels( #creating labels for specific variables
     wdf_q1_4_followup_age = "Respondent's age",
     wdf_q1_4_followup_age_group = "Respondent's age group",
     wdf_q2_3a_b_followup_years = "Duration of diabetes (years)",
     wdf_q2_3a_b_followup_years_group = "Duration of diabetes (years) group",
     wdf_q2_11a_b_followup_years = "Duration of high BP (years)",
     wdf_q2_11a_b_followup_years_group = "Duration of hig BP (years) group",
     wdf_q5_1_2_3a_followup = "Systolic Blood pressure",
     wdf_q5_1_2_3b_followup = "Diastolic Blood pressure",
     wdf_q5_followup_bp = "Blood Pressure (mmHg)",
     wdf_q5_5a_b_followup = "Height in metres",
     wdf_q5_6_7_followup = "Weight in kgs", 
     wdf_q5_5_6_7_followup_bmi = "BMI (kg/m2)",
     wdf_q5_5_6_7_followup_bmi_group = "BMI (kg/m2) group",
     wdf_q5_8a_b_followup_waist_hip_ratio = "Waist-to-hip ratio",
     wdf_q5_8a_b_followup_waist_hip_ratio_group = "Waist-to-hip ratio group",
     wdf_q5_10_followup_group = "Blood glucose (mmol/L) group"
   )


```


```{r diabetes followup final data for analysis, results="hide", include=FALSE}

# make dataset with variables for descriptive and inferential statistics

  diabetes_followup_final_analysis <- diabetes_followup_final_clean%>%
  dplyr::select( #socio-demographics
    wdf_q1_5_followup, wdf_q1_4_followup_age, wdf_q1_4_followup_age_group, wdf_q1_9_followup,
                #History of medical conditions and treatment
    wdf_q2_1_followup, wdf_q2_3a_b_followup_years, wdf_q2_3a_b_followup_years_group, wdf_q2_4_followup, wdf_q2_6_followup:wdf_q2_7f_followup, 
    wdf_q2_8a_followup, wdf_q2_8b_followup, wdf_q2_8c_followup, wdf_q2_8d_followup, wdf_q2_8g_followup,
    wdf_q2_9_followup, wdf_q2_11a_b_followup_years, wdf_q2_11a_b_followup_years_group, wdf_q2_12_followup, wdf_q2_14_followup:wdf_q2_15e_followup,
    wdf_q2_16a_followup, wdf_q2_16b_followup, wdf_q2_16c_followup, wdf_q2_16d_followup, wdf_q2_16g_followup,
    wdf_q2_17a_followup, wdf_q2_17b_followup, wdf_q2_17c_followup, wdf_q2_17d_followup, wdf_q2_17e_followup, wdf_q2_17f_followup, 
    wdf_q2_17g_followup, wdf_q2_17h_followup, wdf_q2_17i_followup, wdf_q2_19a_followup:wdf_q2_19f_followup,
                #Lifestyle history/Health behaviour
    wdf_q3_1_followup:wdf_q3_3_followup, wdf_q3_4_followup, wdf_q3_6_followup:wdf_q3_8_followup, wdf_q3_9_followup, wdf_q3_10_followup, 
    wdf_q3_14_followup, wdf_q3_15_followup, wdf_q3_17a_followup:wdf_q3_17g_followup,
    wdf_q3_32_followup:wdf_q3_33f_followup, wdf_q3_34_followup:wdf_q3_35f_followup, wdf_q3_36_followup:wdf_q3_37f_followup,
    wdf_q3_38_followup:wdf_q3_39e_followup, wdf_q3_40_followup:wdf_q3_41g_followup, wdf_q3_42_followup:wdf_q3_43f_followup,
    wdf_q3_44_followup:wdf_q3_45j_followup, wdf_q3_46_followup:wdf_q3_47h_followup,
                #Clinical and anthropometric measurements
    wdf_q5_0a_followup:wdf_q5_0d_followup, wdf_q5_1_2_3a_followup, wdf_q5_1_2_3b_followup, wdf_q5_followup_bp, wdf_q5_4_followup,
    wdf_q5_5a_b_followup, wdf_q5_6_7_followup, wdf_q5_5_6_7_followup_bmi, wdf_q5_5_6_7_followup_bmi_group,
    wdf_q5_8a_followup, wdf_q5_8b_followup, wdf_q5_8a_b_followup_waist_hip_ratio, wdf_q5_8a_b_followup_waist_hip_ratio_group,
    wdf_q5_10_followup, wdf_q5_10_followup_group, wdf_q5_11_followup
                )


```


```{r saving locally followup final clean data, results="hide", include=FALSE}

#saving final followup data
save(diabetes_followup_final_clean, diabetes_followup_final_analysis, file = "wdffollowup_cleaned_final.RData")


```


# **Introduction**

This study titled [**Improving the lives of diabetics in Nairobi's slum through access to quality health care**](https://microdataportal.aphrc.org/index.php/catalog/75) was under the **Health and Well-Being (HaW) Theme** and aimed to improve the management of diabetes and other comorbidities with emphasis on the use of integrated guidelines and patient empowerment. It was carried out from Individual respondents living in Korogocho and Viwandani informal settlements in Nairobi.


# **Data-Follow up**

Data collected face to face on clinical attendees using 6 months and 12 months (WDF_ 6 follow up - Questionnaire) included:

* Demographic identifiers (respondentID, age and sex).

* history of medical conditions and treatment

* lifestyle history/Health behaviour.

* clinical and anthropometric measurements.


## Data description


```{r data description}


  tbl_summary(diabetes_followup_final_clean%>%dplyr::select(wdf_q1_10_followup, wdf_q1_11_followup, wdf_q1_12_followup,
                                                            wdf_q1_9_followup), 
                     by = wdf_q1_9_followup,
                      type = list(
                        all_dichotomous() ~ "categorical")
                      , digits = list(all_continuous() ~ 2, 
                                      all_categorical() ~ c(0, 1))
                      , missing = "no" #list missing data separately #ifany #no #always
                      ,missing_text = "Missing"
                      ) %>% 
  modify_header(label = "**Descriptives**") %>% # update the column header
  bold_labels() %>%
  italicize_levels()%>%
  add_n( statistic = "{n}", col_label = "**n**", last = FALSE, footnote = FALSE)%>% # add column with total number of non-missing observations
  as_flex_table() #covert gtsummary object to knitrkable object. also use as_flex_table() to maintain identation, footnotes, spanning headers


```

## Data Dictionary

Information about the attributes of diabetes baseline data contains 6 columns namely:

- **pos:** Column position of variable in data
- **variable:** Study variable
- **label:** Description of study variable
- **col_type:** Data type. i.e dbl(numeric variable), fct(categorical variable), date(date variable), chr(character/string variable)
- **levels:** variable levels/categories
- **value_labels:** value of variable categories

```{r data dictionary, results='asis'}

kable(
  diabetes_followup_variable_attr%>%
    mutate(value_labels = diabetes_followup_variable_attr1$value_labels)
  )

```


## Data Analysis

The quantitative data was cleaned and analysed using R version 4.2.3 (2023). 

Descriptive summary statistics in form of frequency, percentage, mean and standard deviation were generated to examine socio-demographic, history of medical conditions and treatment, lifestyle history/Health behaviour and anthropometric measurements variables as a function of data collection round (6month and 12month followup).

The results are presented in narrative and summary tables.

# **Descriptive statistics**

```{r final variables by gender}

  tbl_summary(diabetes_followup_final_analysis,
              by = wdf_q1_9_followup,
                      type = list(
                        all_dichotomous() ~ "categorical"
                         ,all_continuous() ~ "continuous2"
                        )
                      , statistic = all_continuous() ~ c(
                                      "{mean} ({sd})", 
                                      "{median} ({p25}, {p75})", 
                                      "{min}, {max}")
                       , digits = list(all_continuous() ~ 2, 
                                      all_categorical() ~ c(0, 1))
                      ,percent = "column" #"column", "row", or "cell"
                      , missing = "always" #list missing data separately #ifany #no #always
                      ,missing_text = "Missing"
                      ) %>% 
  modify_header(label = "**Variables**") %>% # update the column header
  bold_labels() %>%
  italicize_levels()%>%
  add_n( statistic = "{n}", col_label = "**n**", last = FALSE, footnote = FALSE)%>% # add column with total number of non-missing observations
  modify_spanning_header(c("stat_1", "stat_2") ~ "**Data Collection Round**")%>%
  modify_footnote(
    all_stat_cols() ~ "Mean (SD); Median (IQR); Range; Frequency (%)"
  )%>%
  as_flex_table() #covert gtsummary object to flex table object. 

```











