---
title: "Supermarket data - Items "
author: "Reinpeter"
date: "`r Sys.Date()`"
output:
  word_document: 
    number_sections: yes
  pdf_document:
    number_sections: yes
  html_document:
    toc: yes
    toc_depth: 4
    number_sections: yes
---


```{r setup, results="hide", include=FALSE}

## Set Chunk requirements
knitr::opts_chunk$set(#include = TRUE,
                      echo=FALSE, message = FALSE, warning = FALSE)

options(scipen = 999) #turn off scientific notation for all variables

```


```{r setting working directory, include=FALSE, results = "hide"}

## Setting work directory

setwd(".")

```


```{r loading relevant packages, include=FALSE, results = "hide"}

#library we need
libs_supermarket <- c("googledrive" ,"tidyverse", "haven", "janitor", "knitr",
                            "lubridate", "plotly", "gtsummary", "flextable", "fastDummies")

#install missing libraries

inatalled_libs_supermarket <- libs_supermarket  %in% rownames(installed.packages())
if (any(inatalled_libs_supermarket==F)) {
  install.packages(libs_supermarket[!inatalled_libs_supermarket])
}

#load libraries

invisible(lapply(libs_supermarket, library, character.only=T))

set_gtsummary_theme(list(
  "tbl_summary-fn:percent_fun" = function(x) style_percent(x, digits = 1),
  "tbl_summary-str:categorical_stat" = "{n} ({p}%)"
))
# Setting `Compact` theme
theme_gtsummary_compact()

```


```{r importing saved Rdata files, results="hide", include=FALSE}

#load .Rdata files

supermarket_store_final_list <- list.files(path = ".", pattern = "supermarket_store_final.RData", full.names = TRUE)

#supermarket_store data for assigning variable labels

invisible(lapply(supermarket_store_final_list, load, .GlobalEnv))

```


```{r for assigning variable labels}

#Creating a named vector to quickly assign the variable labels

supermarket_item_labels <- as.data.frame(labelled::generate_dictionary(supermarket_store))%>%
  select(variable, label)%>%
  deframe()

supermarket_item_final_labels <- as.data.frame(labelled::generate_dictionary(supermarket_store_final_clean))%>%
  select(variable, label)%>%
  deframe()

```


```{r googledrive downloading supermarket data, results="hide", include=FALSE}

 drive_auth(#email = "guest360@aphrc.org"
           )
  #drive_user()

  supermarket_item_file_id <- drive_find(shared_drive = c(shared_drive_find(pattern = "Data Science Programs")$id),
           q = c("name contains 'UpdatedretailStoresData.dta'")) #search for a specific set of shared drives, use the query string q
  
  supermarket_item_local_download <- drive_download(supermarket_item_file_id$id, overwrite = TRUE)
  
```


```{r reading supermarket data locally, results="hide", include=FALSE}

  ##Reading the .dta with labelled vector converted to a factor
  supermarket_item <- read_dta(paste0(supermarket_item_local_download$local_path))%>%
  mutate_if(is.labelled, as_factor)%>%
  labelled::set_variable_labels(!!!supermarket_item_labels[names(supermarket_item_labels) %in% names(.)]) #labeling variables from data dictionary

  supermarket_item1 <- read_dta(paste0(supermarket_item_local_download$name))

  supermarket_item_variable_attr <- as.data.frame(labelled::generate_dictionary(supermarket_item))

  supermarket_item_variable_attr1 <- as.data.frame(labelled::look_for(supermarket_item1, labels = TRUE, values = TRUE))

```  


```{r final data, results="hide", include=FALSE}

  supermarket_item_final <- supermarket_item%>%
  mutate(across(c(q5p1a, q5p2a), ~as.numeric(.x)),
         q5p2a = if_else(q5p2a_1 == 1, 0, q5p2a))%>%
  mutate(shelves = ifelse(shelves < 6, "shelf1_5",
                   ifelse(shelves < 11, "shelf6_10",
                   ifelse(shelves < 16, "shelf11_15", "shelf_15ormore"))),
         shelves = factor(shelves, levels = c("shelf1_5", "shelf6_10", "shelf11_15", "shelf_15ormore")),
         q4p1 = ifelse(q4p1 == "Brookside, Tuzo,molo milk and mountain fresh", "Brookside; Tuzo; Molo; Mountain fresh",
                ifelse(q4p1 == "KCC gold crown milk, Daima milk,Lato milk", "KCC; Daima; Lato",
                ifelse(q4p1 == "Lato milk,victory farm yoghurt,daima milk", "Lato; Victory Farm; Daima",
                ifelse(q4p1 == "Fanta soda 300ml,  cocacola soda 1.25 and 2 litres and 1 litre minute maid juice", "Coca Cola; minute maid",
                ifelse(q4p1 == "Molo milk fresh milk", "Molo; Fresh milk",
                ifelse(q4p1 == "Ribena, Lucozade", "Ribena; Lucozade",
                ifelse(q4p1 == "Raha drinking chocolate  Asis premium tea", "Raha; Asis",
                ifelse(str_detect(q4p1, "Salit"), "Salit",
                ifelse(str_detect(q4p1, "Zits"), "Zits",
                ifelse(str_detect(q4p1, "Zesta"), "Zesta", 
                ifelse(str_detect(q4p1, "Yego"), "Yego", 
                ifelse(str_detect(q4p1, "Tuzo"), "Tuzo", 
                ifelse(str_detect(q4p1, "Supa loaf") | str_detect(q4p1, "Super loaf"), "Supa loaf", 
                ifelse(str_detect(q4p1, "Royal bakers"), "Royal bakers",
                ifelse(str_detect(q4p1, "Oreo"), "Oreo", 
                ifelse(str_detect(q4p1, "Nuvita"), "Nuvita", 
                ifelse(str_detect(q4p1, "Mumias sugar"), "Mumias", 
                ifelse(str_detect(q4p1, "Molo milk"), "Molo", 
                ifelse(str_detect(q4p1, "Mac coffee") | str_detect(q4p1, "Maccoffee"), "Mac coffee", 
                ifelse(str_detect(q4p1, "Lyons maid"), "Lyons maid", 
                ifelse(str_detect(q4p1, "Lucozade") | str_detect(q4p1, "Lucuzade"), "Lucozade", 
                ifelse(str_detect(q4p1, "Lato milk"), "Lato", 
                ifelse(str_detect(q4p1, "Knorr"), "Knorr",
                ifelse(str_detect(q4p1, "Kinder joy") | str_detect(q4p1, "Kinderjoy"), "Kinder joy",
                ifelse(str_detect(q4p1, "Kifaru maize flour"), "Kifaru", 
                ifelse(str_detect(q4p1, "Kcc fresh milk"), "KCC", 
                ifelse(str_detect(q4p1, "Juicy fresh sweets"), "Juicy fresh", 
                ifelse(str_detect(q4p1, "Honest"), "Honest",
                ifelse(str_detect(q4p1, "Fresh fry") | str_detect(q4p1, "Fresh Fri") | str_detect(q4p1, "Fresh fri"), "Fresh Fri", 
                ifelse(str_detect(q4p1, "Farmers choice") | str_detect(q4p1, "Farmer's choice") , "Farmers choice", 
                ifelse(str_detect(q4p1, "Fanta") | str_detect(q4p1, "Coca"), "Coca Cola", 
                ifelse(str_detect(q4p1, "Dairyland"), "Dairyland", 
                ifelse(str_detect(q4p1, "Dairymilk") | str_detect(q4p1, "Cadbury"), "Cadbury",
                ifelse(str_detect(q4p1, "Daima"), "Daima",
                ifelse(str_detect(q4p1, "Brookside"), "Brookside",
                ifelse(str_detect(q4p1, "Ajab"), "Ajab", q4p1)))))))))))))))))))))))))))))))))))),
         q4p1 = na_if(q4p1, "") )%>%
  labelled::set_variable_labels(!!!supermarket_item_labels[names(supermarket_item_labels) %in% names(.)]) #labeling variables from data dictionary

```


```{r final subset data, results="hide", include=FALSE}

# Dummy code location
supermarket_item_final_set1 <- supermarket_item_final%>%
  dplyr::select(key, location, q7p2a, food_cat, InformasCat)%>%
  mutate(location = fct_recode(location,
                          "Entrance" = "Entrance (Area within 3m in front of the store entrance (or security barrier))",
                          "Endcap A" = "Endcap A (Endcaps (also known as the end of aisles) that face the front of the s",
                          "Endcap B" = "Endcap B (Endcap B refers to the endcaps that face the back of the store. If a s",
                          "Aisle Medium" = "Aisle Medium (All permanent aisle structures within the store. These include any",
                          "Edge" = "Edge (This location includes anything along the perimeter of the store. This inc",
                          "Island Medium" = "Island Medium (These are temporary displays that are often moved or altered. The",
                          "Checkout side" = "Checkout side (The area alongside and just in front of the checkout – often look",
                          "Checkout edge" = "Checkout edge (The endcap of the checkout which faces the rest of the store.)" )
         )%>%
  fastDummies::dummy_cols(select_columns = c("location", "q7p2a", "food_cat", "InformasCat"),
             ignore_na = TRUE, #ignores any NA values in the column
             remove_selected_columns = TRUE #removes the columns used to generate the dummy columns.
             )%>%
  janitor::clean_names()%>%
  mutate(across(c(location_entrance:location_checkout_edge, q7p2a_whole_grain_cereals:q7p2a_infant_formula,
          food_cat_chocolate_and_sugar_confectionery_energy_bars_sweet_topping_and_desserts:food_cat_sauces_dips_other_seasonings_and_dressings,
          informas_cat_breads_rice_and_rice_products_without_added_fat_sugar_or_salt_noodles:informas_cat_baby_and_toddler_milk_formulae
          ), ~ifelse(.x == 0, "No",
                                 ifelse(.x > 0 , "Yes", .x))),
         across(c(location_entrance:location_checkout_edge, q7p2a_whole_grain_cereals:q7p2a_infant_formula,
          food_cat_chocolate_and_sugar_confectionery_energy_bars_sweet_topping_and_desserts:food_cat_sauces_dips_other_seasonings_and_dressings,
          informas_cat_breads_rice_and_rice_products_without_added_fat_sugar_or_salt_noodles:informas_cat_baby_and_toddler_milk_formulae
                  ), ~factor(.x, levels = c("Yes", "No"))))%>%
  labelled::set_variable_labels(!!!supermarket_item_final_labels[names(supermarket_item_final_labels) %in% names(.)]) #labeling variables from data dictionary


# Dummy code Food/Drink Brands advertised in outlet
supermarket_item_final_set2 <- supermarket_item_final%>%
  dplyr::select(key, q4p1)%>%
  fastDummies::dummy_cols(select_columns = c("q4p1"),
             ignore_na = TRUE, #ignores any NA values in the column
             split = "; ",
             remove_selected_columns = TRUE #removes the columns used to generate the dummy columns.
             )%>%
  janitor::clean_names()%>%
  mutate(across(c(q4p1_4us:q4p1_zits), ~ifelse(.x == 0, "No",
                                 ifelse(.x > 0 , "Yes", .x))),
         across(c(q4p1_4us:q4p1_zits), ~factor(.x, levels = c("Yes", "No"))))%>%
  labelled::set_variable_labels(!!!supermarket_item_final_labels[names(supermarket_item_final_labels) %in% names(.)]) #labeling variables from data dictionary

```


```{r final clean data, results="hide", include=FALSE}

#Final clean data set

supermarket_item_final_clean <- bind_cols(supermarket_item_final, supermarket_item_final_set1%>%dplyr::select(-key),
                                           supermarket_item_final_set2%>%dplyr::select(-key))%>%
  mutate(across(c( q5p1a:q5p1a_96, q5p2a:q5p2a_96, q7p3_1:q7p3_300, level_1:level_3, q4p2b1_1:q4p2b1_300), ~ifelse(.x == 0, "No",
                                 ifelse(.x > 0 , "Yes", .x)) ),
         across(c(q5p1a:q5p1a_96, q5p2a:q5p2a_96, q7p3_1:q7p3_300, level_1:level_3, q4p2b1_1:q4p2b1_300), ~ factor(.x, levels = c("Yes", "No"))),
         q7p5 = fct_na_value_to_level(q7p5, level = "Not with cooked/uncooked category"),
         across(c(q3p5a, q3p7, q3p8, q3p10), ~fct_na_value_to_level(.x, level = "No Advert at location")  ),
    across(c(q5p1a:q5p1a_96, q5p2a:q5p2a_96, q4p1_4us:q4p1_zits, q4p2b1_1:q4p2b1_300), ~as.character(.x)),
         across(c(q5p1a:q5p1a_96, q5p2a:q5p2a_96, q4p1_4us:q4p1_zits, q4p2b1_1:q4p2b1_300), ~ifelse(advert == "No", "No Advert at location", .x)),
         across(c(q5p1a:q5p1a_96, q5p2a:q5p2a_96, q4p1_4us:q4p1_zits, q4p2b1_1:q4p2b1_300), ~factor(.x, levels = c("Yes", "No", "No Advert at location" ))) )%>%
    mutate_if(is.factor, ~fct_drop(.x #, only = c("")
            ))%>% #drop unused factor levels
  labelled::set_variable_labels(!!!supermarket_item_labels[names(supermarket_item_labels) %in% names(.)])%>% #labeling variables from data dictionary
  labelled::set_variable_labels(!!!supermarket_item_final_labels[names(supermarket_item_final_labels) %in% names(.)])%>% #labeling variables from data dictionary
  dplyr::select(county:id, location, location_entrance:location_checkout_edge, locationexists:q7p2a, q7p2a_whole_grain_cereals:q7p2a_infant_formula,
                q7p2b, q7p3, q7p3_1:q7p3_300, q7p3b:depth, q4p1, q4p1_4us:q4p1_zits, q4p2a, q4p2b1, q4p2b1_1:q4p2b1_300, q4p2b2, q4p2c, food_cat,
           food_cat_chocolate_and_sugar_confectionery_energy_bars_sweet_topping_and_desserts:food_cat_sauces_dips_other_seasonings_and_dressings,
           food_cat1:food_cat5, InformasCat, 
           informas_cat_breads_rice_and_rice_products_without_added_fat_sugar_or_salt_noodles:informas_cat_baby_and_toddler_milk_formulae,
           InformasCat1:Prominence_Level) #Arranging columns

```


```{r saving locally supermarket final clean data, results="hide", include=FALSE}

#saving final followup data
write_csv(supermarket_item_final_clean, "UpdatedretailStoresData_clean_by_item.csv", na="")

#saving as .Rdata
save(supermarket_item, supermarket_item_final, supermarket_item_final_clean, file = "supermarket_item_final.RData")

```  


```{r supermarket final data for analysis, results="hide", include=FALSE}

# make dataset with variables for descriptive and inferential statistics

  supermarket_item_final_analysis <- supermarket_item_final_clean%>%
  dplyr::select(
    #Store characteristics
    county, location_entrance:location_checkout_edge, Supermarket_Sizea, SESa, Prominence_Level, TotalAreaMSq,
    #Adverts at store
    advert, q3p5a, q3p7, q3p8, q3p10, q5p1a_0:q5p1a_96, q5p2a_1:q5p2a_96,
    #Food/Drink Types and items sold in outlet
    q7p2a_whole_grain_cereals:q7p2a_infant_formula, q7p3_1:q7p3_300,
    #Types of foods sold in the outlet cooked, uncooked or both
    q7p5,
    #shelve number and level where food products are placed
    shelves, level_1:level_3,
    #Food/Drink Brands and items advertised in outlet
    q4p1_4us:q4p1_zits, q4p2b1_1:q4p2b1_300,
    #WHO AFRO Food category
    food_cat_chocolate_and_sugar_confectionery_energy_bars_sweet_topping_and_desserts:food_cat_sauces_dips_other_seasonings_and_dressings,
    #INFORMA Food category
    food_cat5,
    informas_cat_breads_rice_and_rice_products_without_added_fat_sugar_or_salt_noodles:informas_cat_baby_and_toddler_milk_formulae,
    #Nova classification of foods
    Nova_sales
                )

```


```{r create supemarket ggplot theme}

# Creating own ggplot theme to be reused

supermarket_item_theme <-
    ggplot2::theme_minimal() +
    ggplot2::theme(
      legend.position="none",
  legend.text = element_text(size = 12),
  legend.title = element_text(size = 15, color = "red", face = "bold")
  ,axis.text.y = element_text(angle = 0, size = 14)
  ,axis.text.x = element_text(angle = 0, size = 14),
  #plot.title = element_text(vjust = 0.5, face = "bold", size = 16),
  plot.caption = element_text(angle = 0, size = 12, face = "italic"),
  axis.title.x = element_text(size = 16),
  axis.title.y = element_text(size = 16),
  #axis.line.y = element_line(colour = "black",inherit.blank = FALSE),
  panel.grid.major.y = element_blank(),
  panel.grid.major.x = element_line(color = "grey"),
  panel.grid.minor.x = element_blank()
      )

```

# **Introduction**

This study aimed to assess frequency and level of exposure and the persuasive power and techniques used for adverts and its influence on dietary behaviours. 

# **Data**

Quantitative data collection using INFORMAS tools assessed in door advertising in food outlets/stores.

Data collected included:

* type of food (NOVA classification, WHO)
* size of advertisement
* type of advert Billboard, Poster
* promotional content

## Data description

* The data has `r ncol(supermarket_item)` variables and `r nrow(supermarket_item)` observations.

* Data was transformed to `r ncol(supermarket_item_final_clean)` variables and `r nrow(supermarket_item_final_clean)` observations.

```{r data description}

  tbl_summary(supermarket_item_final_clean%>%
                dplyr::select(key,pilotoractual:consent)%>%
                distinct(key, .keep_all = TRUE)%>%
                dplyr::select(-key), 
                      type = list(
                        all_dichotomous() ~ "categorical")
                      , digits = list(all_continuous() ~ 2, 
                                      all_categorical() ~ c(0, 1))
                      , missing = "no" #list missing data separately #ifany #no #always
                      ,missing_text = "Missing"
                      ) %>% 
  modify_header(label = "**Consent**") %>% # update the column header
  bold_labels() %>%
  italicize_levels()%>%
  add_n( statistic = "{n}", col_label = "**n**", last = FALSE, footnote = FALSE)%>% # add column with total number of non-missing observations
  as_flex_table() #covert gtsummary object to knitrkable object. also use as_flex_table() to maintain identation, footnotes, spanning headers

```

## Data Dictionary

Information about the attributes of supermarket data contains 6 columns namely:

- **pos:** Column position of variable in data
- **variable:** Study variable
- **label:** Description of study variable
- **col_type:** Data type. i.e dbl(numeric variable), fct(categorical variable), date(date variable), chr(character/string variable)
- **levels:** variable levels/categories
- **value_labels:** value of variable categories


```{r data dictionary, results='asis'}

kable(
  supermarket_item_variable_attr%>%
    mutate(value_labels = supermarket_item_variable_attr1$value_labels)
  )

```  

## Data Analysis

The quantitative data was cleaned and analysed using R version 4.2.3 (2023). 

Descriptive summary statistics in form of frequency, percentage, mean and standard deviation were generated to examine all selected variables.

Chi-square test and Fisher's exact test where appropriate were used for categorical data to analyze difference in proportion of all selected variables as a function of county and store size.

For continous data, Wilcoxon rank sum test/Kruskal-Wallis rank sum test where appropriate was used to examine the comparison of county, store size and adverts at location(Yes/No) with continous variables.

The results are presented in narrative and summary tables. Statistical significance was set at p<0.05

  
# **Descriptive statistics**

## Summary Tables

```{r final variables descriptives}

 tbl_summary(supermarket_item_final_analysis, 
                      type = list(
                        all_dichotomous() ~ "categorical"
                        ,all_continuous() ~ "continuous2"
                        )
                      , statistic = all_continuous() ~ c(
                        "{mean} ({sd})",
                        "{median} ({p25}, {p75})",
                        "{min}, {max}")
                      , digits = list(all_continuous() ~ 2, 
                                      all_categorical() ~ c(0, 1))
                      , missing = "always" #list missing data separately #ifany #no #always
                      ,missing_text = "Missing"
                      ) %>% 
  modify_header(label = "**Variables**") %>% # update the column header
  bold_labels() %>%
  italicize_levels()%>%
  add_n( statistic = "{n}", col_label = "**n**", last = FALSE, footnote = FALSE)%>% # add column with total number of non-missing observations
  modify_footnote(
    all_stat_cols() ~ "Mean (SD); Median (IQR); Range; Frequency (%)"
  )%>%
  as_flex_table() #covert gtsummary object to knitrkable object. also use as_flex_table() to maintain identation, footnotes, spanning headers

```  


## Plots

```{r foods/drinks items sold, fig.width=10, fig.height=6}

#Top 20 foods/drinks items sold

supermarket_item_final_analysis%>%
  dplyr::select(q7p3_1:q7p3_300)%>%
  pivot_longer(cols = everything(),
               names_to = "items",
               values_to = "value")%>%
  left_join(as.data.frame(labelled::generate_dictionary(supermarket_item_final_clean))%>%dplyr::select(variable, label), 
            by = c("items" = "variable"))%>%
  mutate(count = 1)%>%
  filter(value=="Yes")%>%
  group_by(items, label, value)%>%
  summarise(count = sum(count), .groups = 'drop')%>%
  mutate(p = round((count/nrow(supermarket_item_final_analysis))*100,1))%>%
  arrange(-count)%>%
  slice_max(count, n=20, with_ties=FALSE)%>% #Top 20 by count
  mutate(label = fct_rev(as_factor(label)))%>%
  ggplot(aes(fill=value, y = count, x=label))+
  geom_bar(position = "dodge", stat = "identity", width=0.8)+
  geom_text(aes(label= paste0(count," (", p,"%)" )), vjust=0.4, hjust=-0.1,
            position = position_dodge(0.9), color="black", size=4.5)+
  #scale_y_continuous(n.breaks = 5)+
  scale_y_continuous(breaks = seq(0, 250, by = 50), limits = c(0, 275))+
  supermarket_item_theme+
  geom_hline(yintercept = 0, color = "black")+
  labs(x= "Food/drink items", y="No. sold", fill="", caption = "N=3669")+
  coord_flip()+
  guides(fill= guide_legend(reverse = TRUE))

```


```{r foods/drinks items advertised, fig.width=10, fig.height=6}

#Top 20 foods/drinks items advertised

supermarket_item_final_analysis%>%
  dplyr::select(q4p2b1_1:q4p2b1_300)%>%
  pivot_longer(cols = everything(),
               names_to = "items",
               values_to = "value")%>%
  left_join(as.data.frame(labelled::generate_dictionary(supermarket_item_final_clean))%>%dplyr::select(variable, label), 
            by = c("items" = "variable"))%>%
  mutate(count = 1)%>%
  filter(value=="Yes")%>%
  group_by(items, label, value)%>%
  summarise(count = sum(count), .groups = 'drop')%>%
  mutate(p = round((count/nrow(supermarket_item_final_analysis[!is.na(supermarket_item_final_analysis$q4p2b1_1),]))*100,1))%>%
  arrange(-count)%>%
  slice_max(count, n=20, with_ties=FALSE)%>% #Top 20 by count
  mutate(label = fct_rev(as_factor(label)))%>%
  ggplot(aes(fill=value, y = count, x=label))+
  geom_bar(position = "dodge", stat = "identity", width=0.8)+
  geom_text(aes(label= paste0(count," (", p,"%)" )), vjust=0.4, hjust=-0.1,
            position = position_dodge(0.9), color="black", size=4.5)+
  #scale_y_continuous(n.breaks = 5)+
  scale_y_continuous(breaks = seq(0, 250, by = 50), limits = c(0, 260))+
  supermarket_item_theme+
  geom_hline(yintercept = 0, color = "black")+
  labs(x= "Food/drink items", y="No. advertised", fill="", caption = "N=3657; 12 Missing")+
  coord_flip()+
  guides(fill= guide_legend(reverse = TRUE))

```


```{r brands advertised, fig.width=10, fig.height=6}

#Top 20 Food/drink brand name advertised

 supermarket_item_final_analysis%>%
  dplyr::select(q4p1_4us:q4p1_zits)%>%
  pivot_longer(cols = everything(),
               names_to = "items",
               values_to = "value")%>%
  left_join(as.data.frame(labelled::generate_dictionary(supermarket_item_final_clean))%>%dplyr::select(variable, label), 
            by = c("items" = "variable"))%>%
  mutate(label = gsub("Food/drink brand name advertised - ", "", label),
         count = 1)%>%
  filter(value=="Yes")%>%
  group_by(items, label, value)%>%
  summarise(count = sum(count), .groups = 'drop')%>%
  mutate(p = round((count/nrow(supermarket_item_final_analysis[!is.na(supermarket_item_final_analysis$q4p1_4us),]))*100,1))%>%
  arrange(-count)%>%
  slice_max(count, n=20, with_ties=FALSE)%>% #Top 20 by count
  mutate(label = fct_rev(as_factor(label)))%>%
  ggplot(aes(fill=value, y = count, x=label))+
  geom_bar(position = "dodge", stat = "identity", width=0.8)+
  geom_text(aes(label= paste0(count," (", p,"%)" )), vjust=0.4, hjust=-0.1,
            position = position_dodge(0.9), color="black", size=4.5)+
  #scale_y_continuous(n.breaks = 5)+
  scale_y_continuous(breaks = seq(0, 250, by = 50), limits = c(0, 250))+
  supermarket_item_theme+
  geom_hline(yintercept = 0, color = "black")+
  labs(x= "Food/drink brand name", y="No. advertised", fill="", caption = "N=3657; 12 Missing")+
  coord_flip()+
  guides(fill= guide_legend(reverse = TRUE))

```


# **Inferential statistics**

## County

```{r final variables by county}

  tbl_summary(supermarket_item_final_analysis%>%dplyr::select(-c(q7p3_1:q7p3_300, q4p2b1_1:q4p2b1_300)),
              by = county,
                      type = list(
                        all_dichotomous() ~ "categorical"
                         ,all_continuous() ~ "continuous2"
                        )
                      , statistic = all_continuous() ~ c(
                                      "{mean} ({sd})", 
                                      "{median} ({p25}, {p75})", 
                                      "{min}, {max}")
                       , digits = list(all_continuous() ~ 2, 
                                      all_categorical() ~ c(0, 1))
                      ,percent = "column" #"column", "row", or "cell"
                      , missing = "always" #list missing data separately #ifany #no #always
                      ,missing_text = "Missing"
                      ) %>% 
  modify_header(label = "**Variables**") %>% # update the column header
  bold_labels() %>%
  italicize_levels()%>%
  add_n( statistic = "{n}", col_label = "**n**", last = FALSE, footnote = FALSE)%>% # add column with total number of non-missing observations
  add_p(pvalue_fun = ~style_pvalue(.x, digits = 3),
        test.args = all_tests("fisher.test") ~ list(simulate.p.value=TRUE)) %>%
   bold_p(t= 0.05) %>% # bold p-values under a given threshold (default 0.05)
  #add_overall() %>%
  #add_difference() %>% #add column for difference between two group, confidence interval, and p-value
  modify_spanning_header(c("stat_1", "stat_2", "stat_3") ~ "**County**")%>%
  #modify_caption("**Table 1. Patient Characteristics**")%>%
  modify_footnote(
    all_stat_cols() ~ "Mean (SD); Median (IQR); Range; Frequency (%)"
  )%>%
  as_flex_table() #covert gtsummary object to flex table object. 

```


## Supermarket Size

```{r final variables by Supermarket Size}

  tbl_summary(supermarket_item_final_analysis%>%dplyr::select(-c(q7p3_1:q7p3_300, q4p2b1_1:q4p2b1_300)),
              by = Supermarket_Sizea,
                      type = list(
                        all_dichotomous() ~ "categorical"
                         ,all_continuous() ~ "continuous2"
                        )
                      , statistic = all_continuous() ~ c(
                                      "{mean} ({sd})", 
                                      "{median} ({p25}, {p75})", 
                                      "{min}, {max}")
                       , digits = list(all_continuous() ~ 2, 
                                      all_categorical() ~ c(0, 1))
                      ,percent = "column" #"column", "row", or "cell"
                      , missing = "always" #list missing data separately #ifany #no #always
                      ,missing_text = "Missing"
                      ) %>% 
  modify_header(label = "**Variables**") %>% # update the column header
  bold_labels() %>%
  italicize_levels()%>%
  add_n( statistic = "{n}", col_label = "**n**", last = FALSE, footnote = FALSE)%>% # add column with total number of non-missing observations
  add_p(pvalue_fun = ~style_pvalue(.x, digits = 3),
        test.args = all_tests("fisher.test") ~ list(simulate.p.value=TRUE)) %>%
   bold_p(t= 0.05) %>% # bold p-values under a given threshold (default 0.05)
  #add_overall() %>%
  #add_difference() %>% #add column for difference between two group, confidence interval, and p-value
  modify_spanning_header(c("stat_1", "stat_2", "stat_3") ~ "**Store Size**")%>%
  #modify_caption("**Table 1. Patient Characteristics**")%>%
  modify_footnote(
    all_stat_cols() ~ "Mean (SD); Median (IQR); Range; Frequency (%)"
  )%>%
  as_flex_table() #covert gtsummary object to flex table object. 

```


## Adverts at location

```{r final variables by Adverts at location}

  tbl_summary(supermarket_item_final_analysis%>%dplyr::select(-c(q7p3_1:q7p3_300, q4p2b1_1:q4p2b1_300)),
              by = advert,
                      type = list(
                        all_dichotomous() ~ "categorical"
                         ,all_continuous() ~ "continuous2"
                        )
                      , statistic = all_continuous() ~ c(
                                      "{mean} ({sd})", 
                                      "{median} ({p25}, {p75})", 
                                      "{min}, {max}")
                       , digits = list(all_continuous() ~ 2, 
                                      all_categorical() ~ c(0, 1))
                      ,percent = "column" #"column", "row", or "cell"
                      , missing = "always" #list missing data separately #ifany #no #always
                      ,missing_text = "Missing"
                      ) %>% 
  modify_header(label = "**Variables**") %>% # update the column header
  bold_labels() %>%
  italicize_levels()%>%
  add_n( statistic = "{n}", col_label = "**n**", last = FALSE, footnote = FALSE)%>% # add column with total number of non-missing observations
  add_p(pvalue_fun = ~style_pvalue(.x, digits = 3),
        test.args = all_tests("fisher.test") ~ list(simulate.p.value=TRUE)) %>%
   bold_p(t= 0.05) %>% # bold p-values under a given threshold (default 0.05)
  #add_overall() %>%
  #add_difference() %>% #add column for difference between two group, confidence interval, and p-value
  modify_spanning_header(c("stat_1", "stat_2") ~ "**Do we have adverts at location**")%>%
  #modify_caption("**Table 1. Patient Characteristics**")%>%
  modify_footnote(
    all_stat_cols() ~ "Mean (SD); Median (IQR); Range; Frequency (%)"
  )%>%
  as_flex_table() #covert gtsummary object to flex table object. 

```












