---
title: "Supermarket data - Adverts "
author: "Reinpeter"
date: "`r Sys.Date()`"
output:
  word_document: 
    number_sections: yes
  pdf_document:
    number_sections: yes
  html_document:
    toc: yes
    toc_depth: 4
    number_sections: yes
---


```{r setup, results="hide", include=FALSE}

## Set Chunk requirements
knitr::opts_chunk$set(#include = TRUE,
                      echo=FALSE, message = FALSE, warning = FALSE)

```


```{r setting working directory, include=FALSE, results = "hide"}

## Setting work directory

setwd(".")

```


```{r loading relevant packages, include=FALSE, results = "hide"}

#library we need
libs_supermarket_advert <- c("googledrive" ,"tidyverse", "haven", "janitor", "knitr",
                            "lubridate", "plotly", "gtsummary", "flextable", "fastDummies", "labelled")

#install missing libraries

inatalled_libs_supermarket_advert <- libs_supermarket_advert  %in% rownames(installed.packages())
if (any(inatalled_libs_supermarket_advert==F)) {
  install.packages(libs_supermarket_advert[!inatalled_libs_supermarket_advert])
}

#load libraries

invisible(lapply(libs_supermarket_advert, library, character.only=T))

set_gtsummary_theme(list(
  "tbl_summary-fn:percent_fun" = function(x) style_percent(x, digits = 1),
  "tbl_summary-str:categorical_stat" = "{n} ({p}%)"
))
# Setting `Compact` theme
theme_gtsummary_compact()

```


```{r importing saved Rdata files, results="hide", include=FALSE}

#load .Rdata files

supermarket_item_final_list <- list.files(path = ".", pattern = "supermarket_item_final.RData", full.names = TRUE)

#supermarket_store data for assigning variable labels

invisible(lapply(supermarket_item_final_list, load, .GlobalEnv))

```


```{r for assigning variable labels}

#Creating a named vector to quickly assign the variable labels

supermarket_advert_labels <- as.data.frame(labelled::generate_dictionary(supermarket_item))%>%
  select(variable, label)%>%
  deframe()

supermarket_advert_final_labels <- as.data.frame(labelled::generate_dictionary(supermarket_item_final_clean))%>%
  select(variable, label)%>%
  deframe()

```


```{r final clean data, results="hide", include=FALSE}

#Final clean data set

supermarket_advert_final_clean <- supermarket_item_final_clean%>%
  filter(advert == "Yes")%>%
    mutate_if(is.factor, ~fct_drop(.x #, only = c("")
            ))

```


```{r saving locally supermarket final clean data, results="hide", include=FALSE}

#saving final followup data
write_csv(supermarket_advert_final_clean, "UpdatedretailStoresData_clean_by_advert.csv", na="")

#saving as .Rdata
save(supermarket_advert_final_clean, file = "supermarket_advert_final.RData")

```  


```{r supermarket final data for analysis, results="hide", include=FALSE}

# make dataset with variables for descriptive and inferential statistics

  supermarket_advert_final_analysis <- supermarket_advert_final_clean%>%
  dplyr::select(
    #consent
    pilotoractual:consent,
    #Store characteristics
    county, location_entrance:location_checkout_edge, locationexists, food, Supermarket_Sizea, SESa, Prominence_Level, TotalAreaMSq,
    #Adverts at store
    advert, q3p5a, q3p7, q3p8, q3p10, q5p1a_0:q5p1a_96, q5p2a_1:q5p2a_96,
    #Food/Drink Types and items sold in outlet
    q7p2a_whole_grain_cereals:q7p2a_infant_formula, q7p3_1:q7p3_300,
    #Types of foods sold in the outlet cooked, uncooked or both
    q7p5,
    #shelve number and level where food products are placed
    shelves, level_1:level_3,
    #Food/Drink Brands and items advertised in outlet
    q4p1_4us:q4p1_zits, q4p2a_whole_grain_cereals:q4p2a_infant_formula, q4p2b1_1:q4p2b1_300,
    #WHO AFRO Food category
    food_cat_chocolate_and_sugar_confectionery_energy_bars_sweet_topping_and_desserts:food_cat_sauces_dips_other_seasonings_and_dressings,
    #INFORMA Food category
    food_cat5,
    informas_cat_breads_rice_and_rice_products_without_added_fat_sugar_or_salt_noodles:informas_cat_baby_and_toddler_milk_formulae,
    #Nova classification of foods
    Nova_sales)%>%
  dplyr::select(-c(q7p3_14, q7p3_25, q7p3_30, q7p3_43, q7p3_49, q7p3_60, q7p3_78, q7p3_87, q7p3_94, q7p3_101, q7p3_115, q7p3_142, q7p3_146, q7p3_149,
                   q7p3_157, q7p3_164, q7p3_170, q7p3_175, q7p3_190, q7p3_198, q7p3_212, q7p3_219, q7p3_234, q7p3_239, q7p3_248, q7p3_252, q7p3_256,
                   q7p3_265, q7p3_283, q7p3_291, q7p3_300, q4p2b1_14, q4p2b1_25, q4p2b1_30, q4p2b1_43, q4p2b1_49, q4p2b1_60, q4p2b1_78, q4p2b1_87,
                   q4p2b1_94, q4p2b1_101, q4p2b1_115, q4p2b1_142, q4p2b1_146, q4p2b1_149, q4p2b1_157, q4p2b1_164, q4p2b1_170, q4p2b1_175, q4p2b1_190,
                   q4p2b1_198, q4p2b1_212, q4p2b1_219, q4p2b1_234, q4p2b1_239, q4p2b1_248, q4p2b1_252, q4p2b1_256, q4p2b1_265, q4p2b1_283, q4p2b1_291,
                   q4p2b1_300, q5p1a_96, q5p2a_96, food_cat_other_dairy_based_desserts,
                   informas_cat_other_high_fat_salt_products_include_meat_fish_bean_paste)) #unselect various "others" variables

```


```{r create supemarket ggplot theme}

# Creating own ggplot theme to be reused

supermarket_advert_theme <-
    ggplot2::theme_minimal() +
    ggplot2::theme(
      legend.position="none",
  legend.text = element_text(size = 12),
  legend.title = element_text(size = 15, color = "red", face = "bold")
  ,axis.text.y = element_text(angle = 0, size = 14)
  ,axis.text.x = element_text(angle = 0, size = 14),
  #plot.title = element_text(vjust = 0.5, face = "bold", size = 16),
  plot.caption = element_text(angle = 0, size = 12, face = "italic"),
  axis.title.x = element_text(size = 16),
  axis.title.y = element_text(size = 16),
  #axis.line.y = element_line(colour = "black",inherit.blank = FALSE),
  panel.grid.major.y = element_blank(),
  panel.grid.major.x = element_line(color = "grey"),
  panel.grid.minor.x = element_blank()
      )

```

# **Introduction**

This study aimed to assess frequency and level of exposure and the persuasive power and techniques used for adverts and its influence on dietary
behaviours. 

# **Data**

Quantitative data collection using INFORMAS tools assessed in door advertising in food outlets/stores.

Data collected included:

* type of food (NOVA classification, WHO)
* size of advertisement
* type of advert Billboard, Poster
* promotional content

## Data description

* Data was transformed to `r ncol(supermarket_advert_final_clean)` variables and `r nrow(supermarket_advert_final_clean)` observations.

```{r data description}

  tbl_summary(supermarket_advert_final_analysis%>%
                dplyr::select(pilotoractual:consent), 
                      type = list(
                        all_dichotomous() ~ "categorical")
                      , digits = list(all_continuous() ~ 2, 
                                      all_categorical() ~ c(0, 1))
                      , missing = "no" #list missing data separately #ifany #no #always
                      ,missing_text = "Missing"
                      ) %>% 
  modify_header(label = "**Consent**") %>% # update the column header
  bold_labels() %>%
  italicize_levels()%>%
  add_n( statistic = "{n}", col_label = "**n**", last = FALSE, footnote = FALSE)%>% # add column with total number of non-missing observations
  as_flex_table() #covert gtsummary object to knitrkable object. also use as_flex_table() to maintain identation, footnotes, spanning headers

```

## Data Dictionary

Information about the attributes of supermarket data contains 6 columns namely:

- **pos:** Column position of variable in data
- **variable:** Study variable
- **label:** Description of study variable
- **col_type:** Data type. i.e dbl(numeric variable), fct(categorical variable), date(date variable), chr(character/string variable)
- **levels:** variable levels/categories
- **value_labels:** value of variable categories


## Data Analysis

The quantitative data was cleaned and analysed using R version 4.2.3 (2023). 

Descriptive summary statistics in form of frequency, percentage, mean and standard deviation were generated to examine all selected variables.

Chi-square test and Fisher's exact test where appropriate were used for categorical data to analyze difference in proportion of all selected variables
as a function of county and store size

For continous data, Wilcoxon rank sum test/Kruskal-Wallis rank sum test where appropriate was used to examine the comparison of county and store size with continous variables.

The results are presented in narrative and summary tables. Statistical significance was set at p<0.05

  
# **Descriptive statistics**

## Summary Tables

```{r final variables descriptives}

 tbl_summary(supermarket_advert_final_analysis%>%
                dplyr::select(-c(pilotoractual:consent)), 
                      type = list(
                        all_dichotomous() ~ "categorical"
                        ,all_continuous() ~ "continuous2"
                        )
                      , statistic = all_continuous() ~ c(
                        "{mean} ({sd})",
                        "{median} ({p25}, {p75})",
                        "{min}, {max}")
                      , digits = list(all_continuous() ~ 2, 
                                      all_categorical() ~ c(0, 1))
                      , missing = "always" #list missing data separately #ifany #no #always
                      ,missing_text = "Missing"
                      ) %>% 
  modify_header(label = "**Variables**") %>% # update the column header
  bold_labels() %>%
  italicize_levels()%>%
  add_n( statistic = "{n}", col_label = "**n**", last = FALSE, footnote = FALSE)%>% # add column with total number of non-missing observations
  modify_footnote(
    all_stat_cols() ~ "Mean (SD); Median (IQR); Range; Frequency (%)"
  )%>%
  as_flex_table() #covert gtsummary object to knitrkable object. also use as_flex_table() to maintain identation, footnotes, spanning headers

```  


## Plots

```{r foods/drinks items sold, fig.width=10, fig.height=6}

#Top 20 foods/drinks items sold

supermarket_advert_final_analysis%>%
  dplyr::select(q7p3_1:q7p3_299)%>%
  pivot_longer(cols = everything(),
               names_to = "items",
               values_to = "value")%>%
  left_join(as.data.frame(labelled::generate_dictionary(supermarket_advert_final_clean))%>%dplyr::select(variable, label), 
            by = c("items" = "variable"))%>%
  mutate(count = 1)%>%
  filter(value=="Yes")%>%
  group_by(items, label, value)%>%
  summarise(count = sum(count), .groups = 'drop')%>%
  mutate(p = round((count/nrow(supermarket_advert_final_analysis))*100,1))%>%
  arrange(-count)%>%
  slice_max(count, n=20, with_ties=FALSE)%>% #Top 20 by count
  mutate(label = fct_rev(as_factor(label)))%>%
  ggplot(aes(fill=value, y = count, x=label))+
  geom_bar(position = "dodge", stat = "identity", width=0.8)+
  geom_text(aes(label= paste0(count," (", p,"%)" )), vjust=0.4, hjust=-0.1,
            position = position_dodge(0.9), color="black", size=4.5)+
  #scale_y_continuous(n.breaks = 5)+
  scale_y_continuous(breaks = seq(0, 100, by = 20), limits = c(0, 115))+
  supermarket_advert_theme+
  geom_hline(yintercept = 0, color = "black")+
  labs(x= "Food/drink product name sold", y="No. of advertisements", fill="", caption = "N=934")+
  coord_flip()+
  guides(fill= guide_legend(reverse = TRUE))

```


```{r foods/drinks items advertised, fig.width=10, fig.height=6}

#Top 20 foods/drinks items advertised

supermarket_advert_final_analysis%>%
  dplyr::select(q4p2b1_1:q4p2b1_299)%>%
  pivot_longer(cols = everything(),
               names_to = "items",
               values_to = "value")%>%
  left_join(as.data.frame(labelled::generate_dictionary(supermarket_advert_final_clean))%>%dplyr::select(variable, label), 
            by = c("items" = "variable"))%>%
  mutate(count = 1)%>%
  filter(value=="Yes")%>%
  group_by(items, label, value)%>%
  summarise(count = sum(count), .groups = 'drop')%>%
  mutate(p = round((count/nrow(supermarket_advert_final_analysis[!is.na(supermarket_advert_final_analysis$q4p2b1_1),]))*100,1))%>%
  arrange(-count)%>%
  slice_max(count, n=20, with_ties=FALSE)%>% #Top 20 by count
  mutate(label = fct_rev(as_factor(label)))%>%
  ggplot(aes(fill=value, y = count, x=label))+
  geom_bar(position = "dodge", stat = "identity", width=0.8)+
  geom_text(aes(label= paste0(count," (", p,"%)" )), vjust=0.4, hjust=-0.1,
            position = position_dodge(0.9), color="black", size=4.5)+
  #scale_y_continuous(n.breaks = 5)+
  scale_y_continuous(breaks = seq(0, 250, by = 50), limits = c(0, 275))+
  supermarket_advert_theme+
  geom_hline(yintercept = 0, color = "black")+
  labs(x= "Food/drink product name advertised", y="No. of items in advertisements", fill="", caption = "N=922; 12 Missing")+
  coord_flip()+
  guides(fill= guide_legend(reverse = TRUE))

```


```{r brands advertised, fig.width=10, fig.height=6}

#Top 20 Food/drink brand name advertised

 supermarket_advert_final_analysis%>%
  dplyr::select(q4p1_4us:q4p1_zits)%>%
  pivot_longer(cols = everything(),
               names_to = "items",
               values_to = "value")%>%
  left_join(as.data.frame(labelled::generate_dictionary(supermarket_advert_final_clean))%>%dplyr::select(variable, label), 
            by = c("items" = "variable"))%>%
  mutate(label = gsub("Food/drink brand name advertised - ", "", label),
         count = 1)%>%
  filter(value=="Yes")%>%
  group_by(items, label, value)%>%
  summarise(count = sum(count), .groups = 'drop')%>%
  mutate(p = round((count/nrow(supermarket_advert_final_analysis[!is.na(supermarket_advert_final_analysis$q4p1_4us),]))*100,1))%>%
  arrange(-count)%>%
  slice_max(count, n=20, with_ties=FALSE)%>% #Top 20 by count
  mutate(label = fct_rev(as_factor(label)))%>%
  ggplot(aes(fill=value, y = count, x=label))+
  geom_bar(position = "dodge", stat = "identity", width=0.8)+
  geom_text(aes(label= paste0(count," (", p,"%)" )), vjust=0.4, hjust=-0.1,
            position = position_dodge(0.9), color="black", size=4.5)+
  #scale_y_continuous(n.breaks = 5)+
  scale_y_continuous(breaks = seq(0, 250, by = 50), limits = c(0, 250))+
  supermarket_advert_theme+
  geom_hline(yintercept = 0, color = "black")+
  labs(x= "Food/drink brand name advertised", y="No. of items in advertisements", fill="", caption = "N=922; 12 Missing")+
  coord_flip()+
  guides(fill= guide_legend(reverse = TRUE))

```


# **Inferential statistics**

## County

```{r final variables by county}

  tbl_summary(supermarket_advert_final_analysis%>%dplyr::select(-c(pilotoractual:consent, q7p3_1:q7p3_299, q4p2b1_1:q4p2b1_299)),
              by = county,
                      type = list(
                        all_dichotomous() ~ "categorical"
                         ,all_continuous() ~ "continuous2"
                        )
                      , statistic = all_continuous() ~ c(
                                      "{mean} ({sd})", 
                                      "{median} ({p25}, {p75})", 
                                      "{min}, {max}")
                       , digits = list(all_continuous() ~ 2, 
                                      all_categorical() ~ c(0, 1))
                      ,percent = "column" #"column", "row", or "cell"
                      , missing = "always" #list missing data separately #ifany #no #always
                      ,missing_text = "Missing"
                      ) %>% 
  modify_header(label = "**Variables**") %>% # update the column header
  bold_labels() %>%
  italicize_levels()%>%
  add_n( statistic = "{n}", col_label = "**n**", last = FALSE, footnote = FALSE)%>% # add column with total number of non-missing observations
  add_p(pvalue_fun = ~style_pvalue(.x, digits = 3),
        test.args = all_tests("fisher.test") ~ list(simulate.p.value=TRUE)) %>%
   bold_p(t= 0.05) %>% # bold p-values under a given threshold (default 0.05)
  #add_overall() %>%
  #add_difference() %>% #add column for difference between two group, confidence interval, and p-value
  modify_spanning_header(c("stat_1", "stat_2", "stat_3") ~ "**County**")%>%
  #modify_caption("**Table 1. Patient Characteristics**")%>%
  modify_footnote(
    all_stat_cols() ~ "Mean (SD); Median (IQR); Range; Frequency (%)"
  )%>%
  as_flex_table() #covert gtsummary object to flex table object. 

```


## Supermarket Size

```{r final variables by Supermarket Size}

  tbl_summary(supermarket_advert_final_analysis%>%dplyr::select(-c(pilotoractual:consent, q7p3_1:q7p3_299, q4p2b1_1:q4p2b1_299)),
              by = Supermarket_Sizea,
                      type = list(
                        all_dichotomous() ~ "categorical"
                         ,all_continuous() ~ "continuous2"
                        )
                      , statistic = all_continuous() ~ c(
                                      "{mean} ({sd})", 
                                      "{median} ({p25}, {p75})", 
                                      "{min}, {max}")
                       , digits = list(all_continuous() ~ 2, 
                                      all_categorical() ~ c(0, 1))
                      ,percent = "column" #"column", "row", or "cell"
                      , missing = "always" #list missing data separately #ifany #no #always
                      ,missing_text = "Missing"
                      ) %>% 
  modify_header(label = "**Variables**") %>% # update the column header
  bold_labels() %>%
  italicize_levels()%>%
  add_n( statistic = "{n}", col_label = "**n**", last = FALSE, footnote = FALSE)%>% # add column with total number of non-missing observations
  add_p(pvalue_fun = ~style_pvalue(.x, digits = 3),
        test.args = all_tests("fisher.test") ~ list(simulate.p.value=TRUE)) %>%
   bold_p(t= 0.05) %>% # bold p-values under a given threshold (default 0.05)
  #add_overall() %>%
  #add_difference() %>% #add column for difference between two group, confidence interval, and p-value
  modify_spanning_header(c("stat_1", "stat_2", "stat_3") ~ "**Store Size**")%>%
  #modify_caption("**Table 1. Patient Characteristics**")%>%
  modify_footnote(
    all_stat_cols() ~ "Mean (SD); Median (IQR); Range; Frequency (%)"
  )%>%
  as_flex_table() #covert gtsummary object to flex table object. 

```




