---
title: "Supermarket data"
author: "Reinpeter"
date: "`r Sys.Date()`"
output:
  word_document: 
    fig_width: 12
    fig_height: 8
    number_sections: yes
  pdf_document:
    fig_width: 12
    fig_height: 8
    number_sections: yes
  html_document:
    toc: yes
    toc_depth: 4
    number_sections: yes
---



```{r setup, results="hide", include=FALSE}

## Set Chunk requirements
knitr::opts_chunk$set(#include = TRUE,
                      echo=FALSE, message = FALSE, warning = FALSE)


```

```{r setting working directory, include=FALSE, results = "hide"}


## Setting work directory

setwd(".")


```

```{r loading relevant packages, include=FALSE, results = "hide"}

#library we need
libs_supermarket <- c("googledrive" ,"tidyverse", "haven", "janitor", "knitr",
                            "lubridate", "plotly", "gtsummary", "flextable")

#install missing libraries

inatalled_libs_supermarket <- libs_supermarket  %in% rownames(installed.packages())
if (any(inatalled_libs_supermarket==F)) {
  install.packages(libs_supermarket[!inatalled_libs_supermarket])
}

#load libraries

invisible(lapply(libs_supermarket, library, character.only=T))

set_gtsummary_theme(list(
  "tbl_summary-fn:percent_fun" = function(x) style_percent(x, digits = 1),
  "tbl_summary-str:categorical_stat" = "{n} ({p}%)"
))
# Setting `Compact` theme
theme_gtsummary_compact()

```


```{r googledrive downloading supermarket data, results="hide", include=FALSE}

 drive_auth(#email = "guest360@aphrc.org"
           )

  #drive_user()

  supermarket_file_id <- drive_find(shared_drive = c(shared_drive_find(pattern = "Data Science Programs")$id),
           q = c("name contains 'UpdatedretailStoresData.dta'")) #search for a specific set of shared drives, use the query string q
  

  supermarket_local_download <- drive_download(supermarket_file_id$id, overwrite = TRUE)
  

```


```{r reading supermarket data locally, results="hide", include=FALSE}

  ##Reading the .dta with labelled vector converted to a factor
  supermarket <- read_dta("UpdatedretailStoresData.dta")%>%
  mutate_if(is.labelled, as_factor)%>%
  labelled::set_variable_labels( #labeling unlabeled variables and relabling for final data dictionary
    Supermarket_Size = "Store Type",
    Supermarket_Sizea = "Store Type",
    SESa = "SESa",
    q5p1a_11 = "q5p2a_11",
    q5p1a_12 = "q5p2a_12",
    q5p2a_11 = "q5p2a_11",
    q4p2b1_296 = "q4p2b1_296",
    q4p2b1_297 = "q4p2b1_297",
    q4p2b1_298 = "q4p2b1_298",
    q4p2b1_299 = "q4p2b1_299",
    q4p2b1_300 = "q4p2b1_300",
    InformasCat = "INFORMA Food category: Core and Non-Core", 
    InformasCat1 = "INFORMA Food category: Core and Non-Core",
    food_cat5 = "INFORMA Food category: Healthy and Unhealthy",
    food_cat7a1 = "INFORMA Food category: Healthy and Unhealthy",
    food_cat = "WHO AFRO Food category",
    food_cat1 = "WHO AFRO Food category",
    q4p1 = "Q4.1: Food/ drink brand name (e.g macdonalds , Carrefour,Cadburys) advertised", 
    q4p2a = "Q4.2: Food/ drink product group advertised",
    q4p2b1 = "Q4.2: Food/ drink product name advertised",
    q5p1a_0 = "Promotional characters - No character present",
    q5p1a_1 = "Promotional characters - Cartoon or company owned character e.g M&Ms",
    q5p1a_2 = "Promotional characters - Licenced character e.g mickey mouse, dora the explorer",
    q5p1a_3 = "Promotional characters - Amateur sports person (  a person playing sports)",
    q5p1a_4 = "Promotional characters - Famous sports person e.g Dennis Oliech",
    q5p1a_5 = "Promotional characters - Sport event",
    q5p1a_6 = "Promotional characters - Celebrity(non sports)",
    q5p1a_7 = "Promotional characters - Movie tie - in e.g shrek",
    q5p1a_8 = "Promotional characters - Historical events (non -sport) e.g Xmas, Ramadhan",
    q5p1a_9 = "Promotional characters - For kids/ youth/adoelscent e.g image of child, great for school lunch etc",
    q5p1a_10 = "Promotional characters - Awards e.g award winning , number 1, best selling",
    q5p1a_96 = "Promotional characters - Others (speicfy)",
    q5p2a_1 = "Premium offers - No premium offers",
    q5p2a_2 = "Premium offers - Game and app downloads",
    q5p2a_3 = "Premium offers - Contests",
    q5p2a_4 = "Premium offers - Buy one get one free or other",
    q5p2a_5 = "Premium offers - 20% extra or other",
    q5p2a_6 = "Premium offers - Limited edition  ( e.g last stock)",
    q5p2a_7 = "Premium offers - Social charity",
    q5p2a_8 = "Premium offers - Gift or collectable",
    q5p2a_9 = "Premium offers - price discount",
    q5p2a_10 = "Premium offers - Loyalty programs",
    q5p2a_96 = "Premium offers - Others specify",
    q7p2a = "Q7.2: Food/ drink product name (group) sold in the outlet",
    q7p2b = "Q7.2: Other name specify sold in the outlet",
    q7p3 = "Q7.3: Food / drink product name sold in the outlet",
    q7p5 = "Q7.5: Types of foods sold in the outlet: Cooked, Uncooked or both",
    q7p6 = "Q7.6: Food product description and Brand Name sold in the outlet: Cooked, Uncooked or both",
    shelves = "Shelve number where the food category is placed",
    level = "level of placed products in entry/exit in relation to height and direction of floor to ceiling",
    level_1 = "level of placed products in entry/exit in relation to height and direction of floor to ceiling: 0 - 100 cm",
    level_2 = "level of placed products in entry/exit in relation to height and direction of floor to ceiling: 100 - 150 cm",
    level_3 = "level of placed products in entry/exit in relation to height and direction of floor to ceiling: 150 - 190 cm"
  )

  supermarket1 <- read_dta("UpdatedretailStoresData.dta") #read_dta(paste0(supermarket_local_download$local_path))

  
  supermarket_variable_attr <- as.data.frame(labelled::generate_dictionary(supermarket))

  supermarket_variable_attr1 <- as.data.frame(labelled::look_for(supermarket1, labels = TRUE, values = TRUE))

  write_csv(supermarket_variable_attr1, "supermarket_variable_attr1.csv")
  
```  


```{r assigning variable labels}

#Creating a named vector to quickly assign the variable labels

supermarket_labels <- supermarket_variable_attr%>%
  select(variable, label)%>%
  deframe()


```


```{r final data, results="hide", include=FALSE}

  supermarket_final <- supermarket%>%
  mutate(across(c(q5p1a_0:q5p1a_96 ,q5p2a_1:q5p2a_96), ~ifelse(.x == 1, "Yes",
                                                         ifelse(.x == 0 , "No", .x))),
         across(c(q5p1a_0:q5p1a_96 ,q5p2a_1:q5p2a_96), ~factor(.x, levels = c("Yes", "No"))))%>%
  mutate(shelves = ifelse(shelves < 6, "shelf1_5",
                   ifelse(shelves < 11, "shelf6_10",
                   ifelse(shelves < 16, "shelf11_15", "shelf_15ormore"))),
         shelves = factor(shelves, levels = c("shelf1_5", "shelf6_10", "shelf11_15", "shelf_15ormore")),
         q4p1 = ifelse(q4p1 == "Brookside, Tuzo,molo milk and mountain fresh", "Brookside Tuzo Molo Mountain fresh",
                ifelse(q4p1 == "KCC gold crown milk, Daima milk,Lato milk", "KCC Daima Lato",
                ifelse(q4p1 == "Lato milk,victory farm yoghurt,daima milk", "Lato Victory farm Daima",
                ifelse(q4p1 == "Fanta soda 300ml,  cocacola soda 1.25 and 2 litres and 1 litre minute maid juice", "Coca cola minute maid",
                ifelse(q4p1 == "Molo milk fresh milk", "Molo fresh milk",
                ifelse(q4p1 == "Ribena, Lucozade", "Ribena Lucozade",
                ifelse(q4p1 == "Raha drinking chocolate  Asis premium tea", "Raha Asis",
                ifelse(str_detect(q4p1, "Salit"), "Salit",
                ifelse(str_detect(q4p1, "Zits"), "Zits",
                ifelse(str_detect(q4p1, "Zesta"), "Zesta", 
                ifelse(str_detect(q4p1, "Yego"), "Yego", 
                ifelse(str_detect(q4p1, "Tuzo"), "Tuzo", 
                ifelse(str_detect(q4p1, "Supa loaf") | str_detect(q4p1, "Super loaf"), "Supa loaf", 
                ifelse(str_detect(q4p1, "Royal bakers"), "Royal bakers",
                ifelse(str_detect(q4p1, "Oreo"), "Oreo", 
                ifelse(str_detect(q4p1, "Nuvita"), "Nuvita", 
                ifelse(str_detect(q4p1, "Mumias sugar"), "Mumias", 
                ifelse(str_detect(q4p1, "Molo milk"), "Molo", 
                ifelse(str_detect(q4p1, "Mac coffee") | str_detect(q4p1, "Maccoffee"), "Mac coffee", 
                ifelse(str_detect(q4p1, "Lyons maid"), "Lyons maid", 
                ifelse(str_detect(q4p1, "Lucozade") | str_detect(q4p1, "Lucuzade"), "Lucozade", 
                ifelse(str_detect(q4p1, "Lato milk"), "Lato", 
                ifelse(str_detect(q4p1, "Knorr"), "Knorr",
                ifelse(str_detect(q4p1, "Kinder joy") | str_detect(q4p1, "Kinderjoy"), "Kinder joy",
                ifelse(str_detect(q4p1, "Kifaru maize flour"), "Kifaru", 
                ifelse(str_detect(q4p1, "Kcc fresh milk"), "KCC", 
                ifelse(str_detect(q4p1, "Juicy fresh sweets"), "Juicy fresh", 
                ifelse(str_detect(q4p1, "Honest"), "Honest",
                ifelse(str_detect(q4p1, "Fresh fry") | str_detect(q4p1, "Fresh Fri") | str_detect(q4p1, "Fresh fri"), "Fresh Fri", 
                ifelse(str_detect(q4p1, "Farmers choice") | str_detect(q4p1, "Farmer's choice") , "Farmers choice", 
                ifelse(str_detect(q4p1, "Fanta") | str_detect(q4p1, "Coca"), "Coca Cola", 
                ifelse(str_detect(q4p1, "Dairyland"), "Dairyland", 
                ifelse(str_detect(q4p1, "Dairymilk") | str_detect(q4p1, "Cadbury"), "Cadbury",
                ifelse(str_detect(q4p1, "Daima"), "Daima",
                ifelse(str_detect(q4p1, "Brookside"), "Brookside",
                ifelse(str_detect(q4p1, "Ajab"), "Ajab", q4p1)))))))))))))))))))))))))))))))))))))%>%
  labelled::set_variable_labels(!!!supermarket_labels[names(supermarket_labels) %in% names(.)]) #labeling variables from data dictionary
   
  
```


```{r final subset data, results="hide", include=FALSE}

# unique columns of data 
supermarket_final_set1 <- supermarket_final%>%
  dplyr::select(county:q5p2b)%>%
  distinct(key, .keep_all = TRUE)


# data to wide format - Types of foods sold in the outlet
supermarket_final_set2 <- supermarket_final%>%
   dplyr::select(key, setofrp2:q7p3)%>%
   dplyr::select(-c(setofrp2, parent_key, oid, q7p2b,q7p3))%>% #Keeping track of unused variables
  # mutate(q7p2a = str_to_lower(q7p2a),
  #        q7p2a = gsub("(", "", q7p2a, fixed = TRUE), # "Fixed = TRUE" disables regex
  #        q7p2a = gsub(")", "", q7p2a, fixed = TRUE))%>% # "Fixed = TRUE" disables regex
  pivot_wider(names_from = q7p2a, values_from = q7p2a,
              values_fn = ~1,
              values_fill = 0,
              names_expand = TRUE, #Forces implicit(unused) factor levels to explicit. be represented in result
              names_prefix = "q7p2a_")%>%
  janitor::clean_names()%>%
  mutate(across(c(!key), ~ifelse(.x == 0, "No",
                                 ifelse(.x > 0 , "Yes", .x))),
         across(c(!key), ~factor(.x, levels = c("Yes", "No"))))%>%
  labelled::set_variable_labels( #labeling new variables
    q7p2a_whole_grain_cereals = "Types of Food/drink sold in the outlet - Whole grain cereals",
    q7p2a_refined_cereals = "Types of Food/drink sold in the outlet - Refined cereals",
    q7p2a_fermented_grain_products = "Types of Food/drink sold in the outlet - Fermented grain products",
    q7p2a_milk_and_milk_products = "Types of Food/drink sold in the outlet - Milk and milk products",
    q7p2a_fresh_juices = "Types of Food/drink sold in the outlet - Fresh juices",
    q7p2a_vitamin_a_rich_fruits = "Types of Food/drink sold in the outlet - Vitamin A rich fruits",
    q7p2a_other_fruits = "Types of Food/drink sold in the outlet - Other fruits",
    q7p2a_nuts_and_seeds = "Types of Food/drink sold in the outlet - Nuts and seeds",
    q7p2a_roots_tubers_plantain_and_potatoes = "Types of Food/drink sold in the outlet - Roots, tubers, plantain and potatoes",
    q7p2a_vitamin_a_rich_vegetables = "Types of Food/drink sold in the outlet - Vitamin A rich vegetables",
    q7p2a_green_leafy_vegetables = "Types of Food/drink sold in the outlet - Green leafy vegetables",
    q7p2a_other_vegetables = "Types of Food/drink sold in the outlet - Other vegetables",
    q7p2a_pulses_beans_peas_lentils = "Types of Food/drink sold in the outlet - Pulses (beans, peas, lentils)",
    q7p2a_soups = "Types of Food/drink sold in the outlet - Soups",
    q7p2a_egg = "Types of Food/drink sold in the outlet - Egg",
    q7p2a_red_meat = "Types of Food/drink sold in the outlet - Red meat",
    q7p2a_organ_meat = "Types of Food/drink sold in the outlet - Organ meat",
    q7p2a_poultry = "Types of Food/drink sold in the outlet - Poultry",
    q7p2a_fish = "Types of Food/drink sold in the outlet - Fish",
    q7p2a_mixed_dishes_vegetarian_meaty = "Types of Food/drink sold in the outlet - Mixed dishes (vegetarian, meaty)",
    q7p2a_savoury_pies = "Types of Food/drink sold in the outlet - Savoury pies",
    q7p2a_processed_meat = "Types of Food/drink sold in the outlet - Processed meat",
    q7p2a_sugar_and_sweet_spreads = "Types of Food/drink sold in the outlet - Sugar and sweet spreads",
    q7p2a_cakes_and_sweets = "Types of Food/drink sold in the outlet - Cakes and sweets",
    q7p2a_oils = "Types of Food/drink sold in the outlet - Oils",
    q7p2a_snacks_savoury_or_sweet = "Types of Food/drink sold in the outlet - Snacks (savoury or sweet)",
    q7p2a_spreading_fats = "Types of Food/drink sold in the outlet - Spreading fats",
    q7p2a_fats = "Types of Food/drink sold in the outlet - Fats",
    q7p2a_sodas_and_sweetened_beverages = "Types of Food/drink sold in the outlet - Sodas and sweetened beverages",
    q7p2a_tea_and_coffee = "Types of Food/drink sold in the outlet - Tea and coffee",
    q7p2a_alcoholic_beverages = "Types of Food/drink sold in the outlet - Alcoholic beverages",
    q7p2a_condiments_and_flavour_cubes = "Types of Food/drink sold in the outlet - Condiments and flavour cubes",
    q7p2a_water = "Types of Food/drink sold in the outlet - Water",
    q7p2a_infant_formula = "Types of Food/drink sold in the outlet - Infant formula"
  )

# data to wide format - Food/Drink items sold in outlet 
supermarket_final_set3 <- supermarket_final%>%
  dplyr::select(key, q7p3_1:q7p3_300, q7p3b)%>%
  dplyr::select(-q7p3b)%>% #Keeping track of unused variables
  group_by(key)%>%
  summarise(across(c(q7p3_1:q7p3_300), ~ sum(.x, na.rm = TRUE)), .groups = "drop")%>%
  mutate(across(c(q7p3_1:q7p3_300), ~ifelse(.x == 0, "No",
                                 ifelse(.x > 0 , "Yes", .x))),
         across(c(q7p3_1:q7p3_300), ~factor(.x, levels = c("Yes", "No"))))%>%
  labelled::set_variable_labels(!!!supermarket_labels[names(supermarket_labels) %in% names(.)]) #labeling variables from data dictionary
  

# data to wide format - Types of foods sold in the outlet cooked, uncooked or both
supermarket_final_set4 <- supermarket_final%>%
  dplyr::select(key, q7p5, q7p6)%>%
  dplyr::select(-q7p6)%>% #Keeping track of unused variables
  pivot_wider(names_from = q7p5, values_from = q7p5,
              values_fn = ~1,
              values_fill = 0,
              names_expand = TRUE, #Forces implicit(unused) factor levels to explicit. be represented in result
              names_prefix = "q7p5_")%>%
  janitor::clean_names()%>%
  dplyr::select(-q7p5_na)%>%
  mutate(across(c(!key), ~ifelse(.x == 0, "No",
                                 ifelse(.x > 0 , "Yes", .x))),
         across(c(!key), ~factor(.x, levels = c("Yes", "No"))))%>%
  labelled::set_variable_labels( #labeling new variables
    q7p5_un_cooked = "Q7.5: Types of foods sold/advertised in the outlet - Uncooked",
    q7p5_cooked = "Q7.5: Types of foods sold/advertised in the outlet - Cooked",
    q7p5_both = "Q7.5: Types of foods sold/advertised in the outlet - Both Uncooked and Cooked"
  )

# data to wide format shelves number where food products are placed
supermarket_final_set5 <- supermarket_final%>%
  dplyr::select(key, shelves:depth)%>%
  dplyr::select(-c(level,length, width, depth))%>% #Keeping track of unused variables
  pivot_wider(names_from = shelves, values_from = shelves,
              values_fn = ~1,
              values_fill = 0,
              names_expand = TRUE, #Forces implicit(unused) factor levels to explicit. be represented in result
              names_prefix = "shelves_")%>%
  dplyr::select(key, shelves_shelf1_5, shelves_shelf6_10, shelves_shelf11_15, shelves_shelf_15ormore, level_1:level_3)%>%
  group_by(key)%>%
  summarise(across(c(shelves_shelf1_5:level_3), ~ sum(.x, na.rm = TRUE)), .groups = "drop")%>%
  mutate(across(c(shelves_shelf1_5:level_3), ~ifelse(.x == 0, "No",
                                 ifelse(.x > 0 , "Yes", .x))),
         across(c(shelves_shelf1_5:level_3), ~factor(.x, levels = c("Yes", "No"))))%>%
  labelled::set_variable_labels(!!!supermarket_labels[names(supermarket_labels) %in% names(.)])%>% #labeling variables from data dictionary
  labelled::set_variable_labels( #labeling new variables
    shelves_shelf1_5 = "Shelve number where the food category is placed: Shelf 1-5",
    shelves_shelf6_10 = "Shelve number where the food category is placed: Shelf 6-10",
    shelves_shelf11_15 = "Shelve number where the food category is placed: Shelf 11-15",
    shelves_shelf_15ormore = "Shelve number where the food category is placed: Shelf 15 or more"
  )

# data to wide format - Food/Drink Brands advertised in outlet
supermarket_final_set6 <- supermarket_final%>%
  dplyr::select(key, q4p1, q4p2a, q4p2b1)%>%
  dplyr::select(-c(q4p2a, q4p2b1))%>% #Keeping track of unused variables
  mutate(q4p1 = na_if(q4p1, ""))%>%
  pivot_wider(names_from = q4p1, values_from = q4p1,
              values_fn = ~1,
              values_fill = 0, 
              names_expand = TRUE, #Forces implicit(unused) factor levels to explicit. be represented in result
              names_prefix = "q4p1_")%>%
  janitor::clean_names()%>%
  dplyr::select(-q4p1_na)%>%
  mutate(q4p1_brookside = q4p1_brookside + q4p1_brookside_tuzo_molo_mountain_fresh,
         q4p1_tuzo = q4p1_tuzo + q4p1_brookside_tuzo_molo_mountain_fresh,
         q4p1_molo = q4p1_tuzo + q4p1_brookside_tuzo_molo_mountain_fresh + q4p1_molo_fresh_milk,
         q4p1_fresh_milk = q4p1_fresh_milk + q4p1_molo_fresh_milk,
         q4p1_mountain_fresh = q4p1_brookside_tuzo_molo_mountain_fresh,
         q4p1_coca_cola = q4p1_coca_cola + q4p1_coca_cola_minute_maid,
         q4p1_minute_maid = q4p1_coca_cola_minute_maid,
         q4p1_daima = q4p1_daima + q4p1_kcc_daima_lato + q4p1_lato_victory_farm_daima,
         q4p1_kcc = q4p1_kcc + q4p1_kcc_daima_lato,
         q4p1_lato = q4p1_lato + q4p1_kcc_daima_lato + q4p1_lato_victory_farm_daima,
         q4p1_victory_farm = q4p1_victory_farm + q4p1_lato_victory_farm_daima,
         q4p1_lucozade = q4p1_lucozade + q4p1_ribena_lucozade,
         q4p1_ribena = q4p1_ribena + q4p1_ribena_lucozade,
         q4p1_raha = q4p1_raha_asis,
         q4p1_asis = q4p1_raha_asis,
         )%>%
  dplyr::select(-q4p1_brookside_tuzo_molo_mountain_fresh, -q4p1_molo_fresh_milk,-q4p1_coca_cola_minute_maid,
                -q4p1_kcc_daima_lato, -q4p1_lato_victory_farm_daima, -q4p1_ribena_lucozade, -q4p1_raha_asis)%>% #deleting unwanted columns
  mutate(across(c(!key), ~ifelse(.x == 0, "No",
                                 ifelse(.x > 0 , "Yes", .x))),
         across(c(!key), ~factor(.x, levels = c("Yes", "No"))))%>%
  labelled::set_variable_labels( #labeling new variables
    q4p1_4us = "Food/drink brand name advertised - 4us",
    q4p1_ajab = "Food/drink brand name advertised - Ajab",
    q4p1_ben_and_jerrys = "Food/drink brand name advertised - Ben and Jerry's",
    q4p1_bio = "Food/drink brand name advertised - Bio",
    q4p1_blueband = "Food/drink brand name advertised - Blueband",
    q4p1_brookside = "Food/drink brand name advertised - Brookside",
    q4p1_cadbury = "Food/drink brand name advertised - Cadbury",
    q4p1_cheeky_treetz = "Food/drink brand name advertised - Cheeky treetz",
    q4p1_club = "Food/drink brand name advertised - Club",
    q4p1_coca_cola = "Food/drink brand name advertised - Coca cola",
    q4p1_creambell = "Food/drink brand name advertised - Creambell",
    q4p1_daima = "Food/drink brand name advertised - Daima",
    q4p1_dairyland = "Food/drink brand name advertised - Dairyland",
    q4p1_dasani = "Food/drink brand name advertised - Dasani",
    q4p1_dawaat = "Food/drink brand name advertised - Dawaat",
    q4p1_delamere = "Food/drink brand name advertised - Delamere",
    q4p1_dido = "Food/drink brand name advertised - Dido",
    q4p1_dormans = "Food/drink brand name advertised - Dormans",
    q4p1_farmers_choice = "Food/drink brand name advertised - Farmer's choice",
    q4p1_fresh_fri = "Food/drink brand name advertised - Fresh Fri",
    q4p1_fresh_milk = "Food/drink brand name advertised - Fresh milk",
    q4p1_honest = "Food/drink brand name advertised - Honest",
    q4p1_i_j = "Food/drink brand name advertised - I&J",
    q4p1_ilara = "Food/drink brand name advertised - Ilara",
    q4p1_indomie = "Food/drink brand name advertised - Indomie",
    q4p1_juicy_fresh = "Food/drink brand name advertised - Juicy fresh",
    q4p1_juicy_fruit = "Food/drink brand name advertised - Juicy fruit",
    q4p1_kabras = "Food/drink brand name advertised - Kabras",
    q4p1_kcc = "Food/drink brand name advertised - KCC",
    q4p1_kenoodles = "Food/drink brand name advertised - Kenoodles",
    q4p1_kifaru = "Food/drink brand name advertised - Kifaru",
    q4p1_kinder_joy = "Food/drink brand name advertised - Kinder joy",
    q4p1_knorr = "Food/drink brand name advertised - Knorr",
    q4p1_lato = "Food/drink brand name advertised - Lato",
    q4p1_lollipop = "Food/drink brand name advertised - Lollipop",
    q4p1_lucozade = "Food/drink brand name advertised - Lucozade",
    q4p1_lyons_maid = "Food/drink brand name advertised - Lyons maid",
    q4p1_mac_coffee = "Food/drink brand name advertised - Mac coffee",
    q4p1_mc_vities = "Food/drink brand name advertised - McVitie's",
    q4p1_molo = "Food/drink brand name advertised - Molo",
    q4p1_mumias = "Food/drink brand name advertised - Mumias",
    q4p1_norda = "Food/drink brand name advertised - Norda",
    q4p1_nut_gold = "Food/drink brand name advertised - Nut gold",
    q4p1_nuvita = "Food/drink brand name advertised - Nuvita",
    q4p1_orbit = "Food/drink brand name advertised - Orbit",
    q4p1_oreo = "Food/drink brand name advertised - Oreo",
    q4p1_p_k = "Food/drink brand name advertised - P.K",
    q4p1_pearl = "Food/drink brand name advertised - Pearl",
    q4p1_pepsi = "Food/drink brand name advertised - Pepsi",
    q4p1_peptang = "Food/drink brand name advertised - Peptang",
    q4p1_postman = "Food/drink brand name advertised - Postman",
    q4p1_ribena = "Food/drink brand name advertised - Ribena",
    q4p1_royal_bakers = "Food/drink brand name advertised - Royal bakers",
    q4p1_salit = "Food/drink brand name advertised - Salit",
    q4p1_savannah = "Food/drink brand name advertised - Savannah",
    q4p1_skittles = "Food/drink brand name advertised - Skittles",
    q4p1_snickers = "Food/drink brand name advertised - Snickers",
    q4p1_supa_loaf = "Food/drink brand name advertised - Supa loaf",
    q4p1_tic_tac = "Food/drink brand name advertised - Tic Tac",
    q4p1_tropical_heat = "Food/drink brand name advertised - Tropical heat",
    q4p1_tuzo = "Food/drink brand name advertised - Tuzo",
    q4p1_urban_bites = "Food/drink brand name advertised - Urban bites",
    q4p1_victory_farm = "Food/drink brand name advertised - Victory Farm",
    q4p1_wrigleys_double_mint = "Food/drink brand name advertised - Wrigleys, double mint",
    q4p1_yego = "Food/drink brand name advertised - Yego",
    q4p1_you_c1000 = "Food/drink brand name advertised - You.C1000",
    q4p1_zesta = "Food/drink brand name advertised - Zesta",
    q4p1_zits = "Food/drink brand name advertised - Zits",
    q4p1_mountain_fresh = "Food/drink brand name advertised - Mountain fresh",
    q4p1_minute_maid = "Food/drink brand name advertised - Minute maid",
    q4p1_raha = "Food/drink brand name advertised - Raha",
    q4p1_asis = "Food/drink brand name advertised - Asis"

  )

# data to wide format - Food/Drink items advertised in outlet 
supermarket_final_set7 <- supermarket_final%>%
  dplyr::select(key, q4p2b1_1:q4p2b1_300)%>%
  group_by(key)%>%
  summarise(across(c(q4p2b1_1:q4p2b1_300), ~ sum(.x, na.rm = TRUE)), .groups = "drop")%>%
  mutate(across(c(q4p2b1_1:q4p2b1_300), ~ifelse(.x == 0, "No",
                                 ifelse(.x > 0 , "Yes", .x))),
         across(c(q4p2b1_1:q4p2b1_300), ~factor(.x, levels = c("Yes", "No"))))%>%
  labelled::set_variable_labels(!!!supermarket_labels[names(supermarket_labels) %in% names(.)]) #labeling variables from data dictionary


# data to wide format - WHO AFRO Food category
supermarket_final_set8 <- supermarket_final%>%
  dplyr::select(key, q4p2b2, q4p2c, food_cat, food_cat1)%>%
  dplyr::select(-c(q4p2b2, q4p2c, food_cat1))%>% #Keeping track of unused variables
  pivot_wider(names_from = food_cat, values_from = food_cat,
              values_fn = ~1,
              values_fill = 0, 
              names_expand = TRUE, #Forces implicit(unused) factor levels to explicit. be represented in result
              names_prefix = "food_cat_")%>%
  janitor::clean_names()%>%
  dplyr::select(-food_cat_na)%>%
  mutate(across(c(!key), ~ifelse(.x == 0, "No",
                                 ifelse(.x > 0 , "Yes", .x))),
         across(c(!key), ~factor(.x, levels = c("Yes", "No"))))%>%
  labelled::set_variable_labels(!!!supermarket_labels[names(supermarket_labels) %in% names(.)])%>% #labeling variables from data dictionary
  labelled::set_variable_labels( #labeling new variables
    food_cat_chocolate_and_sugar_confectionery_energy_bars_sweet_topping_and_desserts = "Chocolate and sugar confectionery, energy bars, sweet topping and desserts",
    food_cat_cakes_sweet_biscuits_and_pastries_other_sweet_bakery_products_dry_mixes_for_making_suchm = "Cakes, sweet biscuits and pastries, other sweet bakery products, dry mixes for making suchm",
    food_cat_bread_bread_products_and_crisp_bread = "Bread, bread products and crisp bread",
    food_cat_breakfast_cereals = "Breakfast cereals",
    food_cat_a_ready_to_use_ready_to_eat_savoury_snacks_potato_cereal_or_starch_based_from_roots_tuber_or_legumes = "a) READY TO USE-ready to eat savoury snacks Potato, cereal or starch-based (from roots, tuber, or legumes)",
    food_cat_b_ready_to_use_processed_nuts_and_edible_seeds = "b) READY TO USE-Processed nuts and edible seeds",
    food_cat_c_ready_to_use_fish_based = "c) READY TO USE-Fish-based",
    food_cat_a_bevarages_juices = "a) BEVARAGES-Juices",
    food_cat_b_bevarages_milk_and_dairy_based_drinks = "b) BEVARAGES-Milk and dairy based drinks",
    food_cat_c_bevarages_water_based_flavoured_and_unflavoured_drink = "c) BEVARAGES-Water- based flavoured and unflavoured drink",
    food_cat_d_bevarages_coffee_coffee_substitutes_tea_herbal_infusions = "d) BEVARAGES-Coffee, coffee substitutes, tea, herbal infusions",
    food_cat_e_bevarages_cereal_legumes_grain_tree_nut_based_beverages = "e) BEVARAGES-Cereal, legumes, grain, tree nut-based beverages",
    food_cat_frozen_dairy_based_desserts_and_edible_ices = "Frozen dairy-based desserts and edible ices",
    food_cat_other_dairy_based_desserts = "Other dairy based desserts",
    food_cat_cheese_and_analogues = "Cheese and analogues",
    food_cat_composite_foods_prepared_foods_ready_made_and_convenience_foods_and_composite_dishes = "Composite foods (Prepared foods, ready-made and convenience foods and composite dishes)",
    food_cat_butter_and_other_fats_and_oils_and_fat_emulsions = "Butter and other fats and oils, and fat emulsions",
    food_cat_pasta_and_noodles_and_like_products_rice_and_grains = "Pasta and noodles and like products, rice and grains",
    food_cat_fresh_and_frozen_meat_poultry_game_fish_and_seafood_a_processed_meat_poultry_and_game_products = "Fresh and frozen meat, poultry, game, fish and seafood--a) Processed meat, poultry and game products",
    food_cat_fresh_and_frozen_meat_poultry_game_fish_and_seafood_b_processed_fish_and_seafood_products = "Fresh and frozen meat, poultry, game, fish and seafood--b) Processed fish and seafood products",
    food_cat_fresh_and_frozen_fruits_and_vegetables_legumes_roots_and_tubersu = "Fresh and frozen fruits and vegetables, legumes, roots and tubersu",
    food_cat_processed_fruits_vegetables_and_legumes = "Processed fruits, vegetables, and legumes",
    food_cat_solid_form_soybean_products = "Solid-form soybean products",
    food_cat_sauces_dips_other_seasonings_and_dressings = "Sauces, dips, other seasonings and dressings"
  )


# data to wide format - INFORMA Food category: Healthy and Unhealthy
supermarket_final_set9 <- supermarket_final%>%
  dplyr::select(key, food_cat5, food_cat7a1)%>%
  dplyr::select(-food_cat7a1)%>% #Keeping track of unused variables
  pivot_wider(names_from = food_cat5, values_from = food_cat5,
              values_fn = length,
              values_fill = 0,
              names_expand = TRUE, #Forces implicit(unused) factor levels to explicit. be represented in result
              names_prefix = "food_cat5_")%>%
  janitor::clean_names()%>%
  dplyr::select(-food_cat5_na)%>%
  mutate(across(c(!key), ~ifelse(.x == 0, "No",
                                 ifelse(.x > 0 , "Yes", .x))),
         across(c(!key), ~factor(.x, levels = c("Yes", "No"))))%>%
  labelled::set_variable_labels( #labeling new variables
    food_cat5_healthy = "INFORMA Food category: Healthy",
    food_cat5_unhealthy = "INFORMA Food category: Unhealthy"
  )


# data to wide format - INFORMA food category: Core and Non-Core
supermarket_final_set10 <- supermarket_final%>%
  dplyr::select(key, InformasCat, InformasCat1)%>%
  dplyr::select(-InformasCat1)%>% #Keeping track of unused variables
  pivot_wider(names_from = InformasCat, values_from = InformasCat,
              values_fn = length,
              values_fill = 0,
              names_expand = TRUE, #Forces implicit(unused) factor levels to explicit. be represented in result
              names_prefix = "InformasCat_")%>%
  janitor::clean_names()%>%
  mutate(across(c(!key), ~ifelse(.x == 0, "No",
                                 ifelse(.x > 0 , "Yes", .x))),
         across(c(!key), ~factor(.x, levels = c("Yes", "No"))))%>%
  labelled::set_variable_labels( #labeling new variables
    informas_cat_breads_rice_and_rice_products_without_added_fat_sugar_or_salt_noodles = "Breads, rice and rice products without added fat, sugar or salt, noodles",
    informas_cat_low_sugar_and_high_fibre_breakfast_cereals_20g_sugar_100g_and_5g_dietary_fibre_100g = "Low sugar and high fibre breakfast cereals (<20g sugar /100g and >5g dietary fibre /100g)",
    informas_cat_fruits_and_fruit_products_without_added_fats_sugars_or_salt = "Fruits and fruit products without added fats, sugars or salt",
    informas_cat_vegetables_and_vegetable_products_without_added_fats_sugars_or_salt = "Vegetables and vegetable products without added fats, sugars or salt",
    informas_cat_milks_and_yoghurts_3g_fat_100g_cheese_15g_fat_100g_and_their_alternatives = "Milks and yoghurts (≤3g fat /100g), cheese (≤15g fat /100g) and their alternatives",
    informas_cat_meat_and_meat_alternatives_include_meat_poultry_fish_legumes_tofu_eggs_and_raw_unsalted_nuts = "Meat and meat alternatives - include meat, poultry, fish, legumes, tofu, eggs and raw unsalted nuts",
    informas_cat_oils_high_in_mono_or_polyunsaturated_fats_and_low_fat_savoury_sauces_10g_fat_100g = "Oils high in mono- or polyunsaturated fats, and low fat savoury sauces (<10g fat /100g)",
    informas_cat_low_fat_salt_meals_include_frozen_or_packaged_meals_6g_saturated_fat_serve_900mg_sodium_serve = "Low fat/salt meals - include frozen or packaged meals (≤6g saturated fat /serve, ≤900mg sodium /serve)",
    informas_cat_healthy_snacks_must_be_based_on_core_foods = "Healthy Snacks – must be based on core foods",
    informas_cat_baby_foods_exclude_milk_formulae = "Baby foods (exclude milk formulae)",
    informas_cat_bottled_water_include_unflavoured_mineral_and_soda_waters = "Bottled water (include unflavoured mineral and soda waters)",
    informas_cat_high_sugar_and_or_low_fibre_breakfast_cereals_20g_sugars_100g_or_5g_dietary_fibre_100g = "High sugar and/or low fibre breakfast cereals (>20g sugars /100g or <5g dietary fibre /100g)",
    informas_cat_flavoured_fried_instant_rice_and_noodle_products = "Flavoured/fried instant rice and noodle products",
    informas_cat_sweet_breads_cakes_muffins_sweet_buns_sweet_biscuits_sweet_glutinous_rice_balls_or_cakes_high_fat_savoury_biscuits_pies_and_pastries = "Sweet breads, cakes, muffins, sweet buns, sweet biscuits, sweet glutinous rice balls or cakes, high fat savoury biscuits",
    informas_cat_meat_and_meat_alternatives_processed_or_preserved_in_salt = "Meat and meat alternatives processed or preserved in salt",
    informas_cat_sweet_snack_foods = "Sweet snack foods",
    informas_cat_savoury_snack_foods_added_salt_or_fat = "Savoury snack foods (added salt or fat)",
    informas_cat_fruit_juice_drinks_98_percent_fruit = "Fruit juice/drinks (<98% fruit)",
    informas_cat_full_cream_milks_and_yoghurts_3g_fat_100g_and_cheese = "Full cream milks and yoghurts (> 3g fat /100g) and cheese",
    informas_cat_ice_cream_iced_confection_and_desserts = "Ice cream, iced confection and desserts",
    informas_cat_chocolate_and_candy_includes_marshmallows_sugar_all_types = "Chocolate and candy - includes marshmallows, sugar (all types)",
    informas_cat_fast_food_not_only_healthier_options_advertised = "Fast food (not only healthier options advertised)",
    informas_cat_high_fat_salt_meals_frozen_or_packaged_meals_6g_saturated_fat_serve_900mg_sodium_serve = "High fat/salt meals - frozen or packaged meals (>6g saturated fat /serve, >900mg sodium /serve)",
    informas_cat_other_high_fat_salt_products_include_meat_fish_bean_paste = "Other high fat/salt products – include meat/fish/bean paste",
    informas_cat_sugar_sweetened_drinks_include_soft_drinks_sweetened_tea_drinks = "Sugar sweetened drinks - include soft drinks, sweetened tea drinks",
    informas_cat_alcohol = "Alcohol",
    informas_cat_recipe_additions_including_soup_cubes_oils_dried_herbs_and_seasonings = "Recipe additions (including soup cubes, oils, dried herbs and seasonings)",
    informas_cat_vitamin_mineral_or_other_dietary_supplements_and_sugar_free_chewing_gum = "Vitamin/mineral or other dietary supplements, and sugar-free chewing gum",
    informas_cat_tea_and_coffee_excluding_sweetened_powder_based_teas_or_coffees = "Tea and coffee (excluding sweetened powder-based teas or coffees)",
    informas_cat_baby_and_toddler_milk_formulae = "Baby and toddler milk formulae"
  )


# data to wide format - Nova Sales
supermarket_final_set11 <- supermarket_final%>%
  dplyr::select(key, food_cat4, Nova_sales, Nova_sales1, food_cat6)%>%
  dplyr::select(-c(food_cat4, Nova_sales1, food_cat6))%>% #Keeping track of unused variables
  pivot_wider(names_from = Nova_sales, values_from = Nova_sales,
              values_fn = length,
              values_fill = 0,
              names_expand = TRUE, #Forces implicit(unused) factor levels to explicit. be represented in result
              names_prefix = "Nova_sales_")%>%
  janitor::clean_names()%>%
  mutate(across(c(!key), ~ifelse(.x == 0, "No",
                                 ifelse(.x > 0 , "Yes", .x))),
         across(c(!key), ~factor(.x, levels = c("Yes", "No"))))

# data to wide format - Store characteristics

supermarket_final_set12 <- supermarket_final%>%
  dplyr::select(key, Supermarket_Sizea, SESa, Prominence_Level)%>%
  mutate(Prominence_Level = str_to_lower(Prominence_Level),
         Prominence_Level = gsub(" ", "_", Prominence_Level))%>%
  pivot_wider(names_from = Prominence_Level, values_from = Prominence_Level,
              values_fn = length,
              values_fill = 0,
              names_expand = TRUE, #Forces implicit(unused) factor levels to explicit. be represented in result
              names_prefix = "Prominence_Level_")%>%
  mutate(across(!c(key, Supermarket_Sizea, SESa ), ~ifelse(.x == 0, "No",
                                 ifelse(.x > 0 , "Yes", .x))),
         across(!c(key, Supermarket_Sizea, SESa), ~factor(.x, levels = c("Yes", "No"))))%>%
  labelled::set_variable_labels(!!!supermarket_labels[names(supermarket_labels) %in% names(.)]) #labeling variables from data dictionary


```


```{r final clean data, results="hide", include=FALSE}

supermarket_final_clean <- purrr::reduce(list(supermarket_final_set1, supermarket_final_set2, supermarket_final_set3,
                                              supermarket_final_set4, supermarket_final_set5, supermarket_final_set6,
                                              supermarket_final_set7, supermarket_final_set8, supermarket_final_set9,
                                              supermarket_final_set10, supermarket_final_set11, supermarket_final_set12),
                                         dplyr::left_join, by = 'key')


```


```{r saving locally supermarket final clean data, results="hide", include=FALSE}

#saving final followup data
write_csv(supermarket_final_clean, "UpdatedretailStoresData_clean.csv", na="")

```  


```{r supermarket final data for analysis, results="hide", include=FALSE}

# make dataset with variables for descriptive and inferential statistics

  supermarket_final_analysis <- supermarket_final_clean%>%
  dplyr::select(
    #Store characteristics
    county, checkouts, location, locationexists, food, Supermarket_Sizea, SESa, Prominence_Level_high_prominence, Prominence_Level_low_prominence,
    Prominence_Level_medium_prominence,
    #Adverts at store
    advert, q3p1, q3p5a, q3p7, q3p8, q3p10, q5p1a_0:q5p1a_12, q5p2a_1:q5p2a_96,
    #Food/Drink Types and items sold in outlet
    q7p2a_whole_grain_cereals:q7p2a_infant_formula, q7p3_1:q7p3_300,
    #Types of foods sold in the outlet cooked, uncooked or both
    q7p5_cooked:q7p5_both, 
    #shelve number and level where food products are placed
    shelves_shelf1_5:level_3,
    #Food/Drink Brands and items advertised in outlet
    q4p1_4us:q4p1_asis, q4p2b1_1:q4p2b1_300,
    #WHO AFRO Food category
    food_cat_chocolate_and_sugar_confectionery_energy_bars_sweet_topping_and_desserts:food_cat_sauces_dips_other_seasonings_and_dressings,
    #INFORMA Food category
    food_cat5_healthy, food_cat5_unhealthy,
    informas_cat_breads_rice_and_rice_products_without_added_fat_sugar_or_salt_noodles:informas_cat_baby_and_toddler_milk_formulae,
    #Nova Sales
    nova_sales_processed_culinary_ingredient:nova_sales_ultraprocessed_foods
                )

```


```{r create supemarket ggplot theme}

# Creating own ggplot theme to be reused

supermarket_theme <-
    ggplot2::theme_minimal() +
    ggplot2::theme(
      legend.position="none",
  legend.text = element_text(size = 12),
  legend.title = element_text(size = 15, color = "red", face = "bold")
  ,axis.text.y = element_text(angle = 0, size = 14)
  ,axis.text.x = element_text(angle = 0, size = 14),
  #plot.title = element_text(vjust = 0.5, face = "bold", size = 16),
  plot.caption = element_text(angle = 0, size = 12, face = "italic"),
  axis.title.x = element_text(size = 16),
  axis.title.y = element_text(size = 16),
  #axis.line.y = element_line(colour = "black",inherit.blank = FALSE),
  panel.grid.major.y = element_blank(),
  panel.grid.major.x = element_line(color = "grey"),
  panel.grid.minor.x = element_blank()
      )

```

# **Introduction**


# **Data**



## Data description

```{r data description}

  tbl_summary(supermarket_final_clean%>%dplyr::select(pilotoractual:consent), 
                      type = list(
                        all_dichotomous() ~ "categorical")
                      , missing = "no" #list missing data separately #ifany #no #always
                      ,missing_text = "Missing"
                      ) %>% 
  modify_header(label = "**Descriptives**") %>% # update the column header
  bold_labels() %>%
  italicize_levels()%>%
  add_n( statistic = "{n}", col_label = "**n**", last = FALSE, footnote = FALSE)%>% # add column with total number of non-missing observations
  as_flex_table() #covert gtsummary object to knitrkable object. also use as_flex_table() to maintain identation, footnotes, spanning headers


```

## Data Dictionary

Information about the attributes of supermarket data contains 6 columns namely:

- **pos:** Column position of variable in data
- **variable:** Study variable
- **label:** Description of study variable
- **col_type:** Data type. i.e dbl(numeric variable), fct(categorical variable), date(date variable), chr(character/string variable)
- **levels:** variable levels/categories
- **value_labels:** value of variable categories


```{r data dictionary, results='asis'}

kable(
  supermarket_variable_attr%>%
    mutate(value_labels = supermarket_variable_attr1$value_labels)
  )

```  

## Data Analysis

The quantitative data was cleaned and analysed using R version 4.2.3 (2023). 

Descriptive summary statistics in form of frequency, percentage, mean and standard deviation were generated to examine all selected variables.

Chi-square test and Fisher's exact test where appropriate were used for categorical data to analyze difference in proportion of all selected variables as a function of county and store size.

The results are presented in narrative and summary tables. Statistical significance was set at p<0.05

  
  
# **Descriptive statistics**

## Summary Tables

```{r final variables descriptives}

 tbl_summary(supermarket_final_analysis, 
                      type = list(
                        all_dichotomous() ~ "categorical"
                        ,all_continuous() ~ "continuous2"
                        )
                      , statistic = all_continuous() ~ c(
                        "{mean} ({sd})",
                        "{median} ({p25}, {p75})",
                        "{min}, {max}" )
                      , digits = list(all_continuous() ~ 2, 
                                      all_categorical() ~ c(0, 1))
                      , missing = "always" #list missing data separately #ifany #no #always
                      ,missing_text = "Missing"
                      ) %>% 
  modify_header(label = "**Variables**") %>% # update the column header
  bold_labels() %>%
  italicize_levels()%>%
  add_n( statistic = "{n}", col_label = "**n**", last = FALSE, footnote = FALSE)%>% # add column with total number of non-missing observations
  modify_footnote(
    all_stat_cols() ~ "Mean (SD); Median (IQR); Range; Frequency (%)"
  )%>%
  as_flex_table() #covert gtsummary object to knitrkable object. also use as_flex_table() to maintain identation, footnotes, spanning headers


```  


## Plots

```{r foods/drinks items sold, fig.width=10, fig.height=6}

#Top 20 foods/drinks items sold

supermarket_final_analysis%>%
  dplyr::select(q7p3_1:q7p3_300)%>%
  pivot_longer(cols = everything(),
               names_to = "items",
               values_to = "value")%>%
  left_join(supermarket_variable_attr%>%dplyr::select(variable, label), 
            by = c("items" = "variable"))%>%
  mutate(count = 1)%>%
  filter(value=="Yes")%>%
  group_by(items, label, value)%>%
  summarise(count = sum(count), .groups = 'drop')%>%
  mutate(p = round((count/nrow(supermarket_final_analysis))*100,1))%>%
  arrange(-count)%>%
  slice_max(count, n=20)%>% #Top 20 by count
  mutate(label = fct_rev(as_factor(label)))%>%
  ggplot(aes(fill=value, y = count, x=label))+
  geom_bar(position = "dodge", stat = "identity", width=0.8)+
  geom_text(aes(label= paste0(count," (", p,"%)" )), vjust=0.4, hjust=-0.1,
            position = position_dodge(0.9), color="black", size=4.5)+
  #scale_y_continuous(n.breaks = 5)+
  scale_y_continuous(breaks = seq(0, 110, by = 10), limits = c(0, 125))+
  supermarket_theme+
  geom_hline(yintercept = 0, color = "black")+
  labs(x= "food/drink items sold", y="n", fill="", caption = "N=114")+
  coord_flip()+
  guides(fill= guide_legend(reverse = TRUE))

```


```{r foods/drinks items advertised, fig.width=10, fig.height=6}

#Top 20 foods/drinks items advertised

supermarket_final_analysis%>%
  dplyr::select(q4p2b1_1:q4p2b1_300)%>%
  pivot_longer(cols = everything(),
               names_to = "items",
               values_to = "value")%>%
  left_join(supermarket_variable_attr%>%dplyr::select(variable, label), 
            by = c("items" = "variable"))%>%
  mutate(count = 1)%>%
  filter(value=="Yes")%>%
  group_by(items, label, value)%>%
  summarise(count = sum(count), .groups = 'drop')%>%
  mutate(p = round((count/nrow(supermarket_final_analysis))*100,1))%>%
  arrange(-count)%>%
  slice_max(count, n=20)%>% #Top 20 by count
  mutate(label = fct_rev(as_factor(label)))%>%
  ggplot(aes(fill=value, y = count, x=label))+
  geom_bar(position = "dodge", stat = "identity", width=0.8)+
  geom_text(aes(label= paste0(count," (", p,"%)" )), vjust=0.4, hjust=-0.1,
            position = position_dodge(0.9), color="black", size=4.5)+
  #scale_y_continuous(n.breaks = 5)+
  scale_y_continuous(breaks = seq(0, 50, by = 10), limits = c(0, 55))+
  supermarket_theme+
  geom_hline(yintercept = 0, color = "black")+
  labs(x= "food/drink items advertised", y="n", fill="", caption = "N=114")+
  coord_flip()+
  guides(fill= guide_legend(reverse = TRUE))

```

  
# **Inferential statistics**

## County

```{r final variables by county}

  tbl_summary(supermarket_final_analysis%>%dplyr::select(-c(q7p3_1:q7p3_300, q4p2b1_1:q4p2b1_300)),
              by = county,
                      type = list(
                        all_dichotomous() ~ "categorical"
                         ,all_continuous() ~ "continuous2"
                        )
                      , statistic = all_continuous() ~ c(
                                      "{mean} ({sd})", 
                                      "{median} ({p25}, {p75})", 
                                      "{min}, {max}")
                       , digits = list(all_continuous() ~ 2, 
                                      all_categorical() ~ c(0, 1))
                      ,percent = "column" #"column", "row", or "cell"
                      , missing = "always" #list missing data separately #ifany #no #always
                      ,missing_text = "Missing"
                      ) %>% 
  modify_header(label = "**Variables**") %>% # update the column header
  bold_labels() %>%
  italicize_levels()%>%
  add_n( statistic = "{n}", col_label = "**n**", last = FALSE, footnote = FALSE)%>% # add column with total number of non-missing observations
  add_p(pvalue_fun = ~style_pvalue(.x, digits = 3),
        test.args = c(location) ~ list(simulate.p.value=TRUE)) %>%
   bold_p(t= 0.05) %>% # bold p-values under a given threshold (default 0.05)
  #add_overall() %>%
  #add_difference() %>% #add column for difference between two group, confidence interval, and p-value
  modify_spanning_header(c("stat_1", "stat_2", "stat_3") ~ "**County**")%>%
  #modify_caption("**Table 1. Patient Characteristics**")%>%
  modify_footnote(
    all_stat_cols() ~ "Mean (SD); Median (IQR); Range; Frequency (%)"
  )%>%
  as_flex_table() #covert gtsummary object to flex table object. 

```

## Supermarket Size

```{r final variables by Supermarket Size}

  tbl_summary(supermarket_final_analysis%>%dplyr::select(-c(q7p3_1:q7p3_300, q4p2b1_1:q4p2b1_300)),
              by = Supermarket_Sizea,
                      type = list(
                        all_dichotomous() ~ "categorical"
                         ,all_continuous() ~ "continuous2"
                        )
                      , statistic = all_continuous() ~ c(
                                      "{mean} ({sd})", 
                                      "{median} ({p25}, {p75})", 
                                      "{min}, {max}")
                       , digits = list(all_continuous() ~ 2, 
                                      all_categorical() ~ c(0, 1))
                      ,percent = "column" #"column", "row", or "cell"
                      , missing = "always" #list missing data separately #ifany #no #always
                      ,missing_text = "Missing"
                      ) %>% 
  modify_header(label = "**Variables**") %>% # update the column header
  bold_labels() %>%
  italicize_levels()%>%
  add_n( statistic = "{n}", col_label = "**n**", last = FALSE, footnote = FALSE)%>% # add column with total number of non-missing observations
  add_p(pvalue_fun = ~style_pvalue(.x, digits = 3),
        test.args = c(location) ~ list(simulate.p.value=TRUE)) %>%
   bold_p(t= 0.05) %>% # bold p-values under a given threshold (default 0.05)
  #add_overall() %>%
  #add_difference() %>% #add column for difference between two group, confidence interval, and p-value
  modify_spanning_header(c("stat_1", "stat_2", "stat_3") ~ "**Store Size**")%>%
  #modify_caption("**Table 1. Patient Characteristics**")%>%
  modify_footnote(
    all_stat_cols() ~ "Mean (SD); Median (IQR); Range; Frequency (%)"
  )%>%
  as_flex_table() #covert gtsummary object to flex table object. 

```




















